### 2023-10-09 proposal/proposal.tex
discussion added

\documentclass[12pt]{article}

\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}

\usepackage{lipsum}
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

\title{Proposal: Something Interesting}
\author{Carol Li\\
  University of Connecticut
}

\begin{document}
\maketitle

\paragraph{Introduction}
Weather catastrophes, including hurricanes, tornados, wildfires, hail storms, and other extreme weather events, have been increasingly 
prevalent and severe in recent years. These events pose significant risks to homeowners and carry substantial financial implications. 
This research proposal aims to investigate how the frequency and severity of weather catastrophes impact the pricing of property 
insurance policies and to identify strategies that can be developed to mitigate the financial burden on homeowners. Previous studies 
in the field \citep[e.g.,][]{kraehnert2021} have provided valuable insights, and we seek to build upon their findings.

\paragraph{Specific Aims}
Our study focuses on three main objectives pertaining to weather catastrophes and property insurance pricing. To start with, we seek 
to explore the overarching research query: ``What is the impact of weather catastrophe frequency and severity on home insurance policy 
prices, and how can homeowners alleviate financial strain?`` This fundamental inquiry will serve as the basis for our investigation.

To examine this question thoroughly, we intend to analyze how variations in insured loss over time correlate with changes in both the 
frequency and severity of weather catastrophes such as hurricanes, tornados, wildfires, and hail storms. By studying these factors' 
influence on policy pricing fluctuations, we aim to gain a comprehensive understanding of their interplay.

Moreover, we plan to convert this primary research question into specific statistical inquiries that employ data science techniques. 
These focused queries include evaluating whether there exists a correlation between weather catastrophe occurrence rates and 
alterations in insured loss over time. Additionally, through data-driven analysis methods, we aim to identify effective strategies 
for alleviating homeowners' financial burdens caused by these catastrophic events.

By successfully achieving these aims through quantitative methodologies rooted in data science principles, our research endeavors 
hold promise for providing valuable insights that can inform practices within the insurance industry. Finally, this knowledge has 
potential implications for public policy decisions aimed at enhancing disaster resilience amidst escalating climate-related risks.

\paragraph{Data}
We will primarily rely on information acquired from reputable sources for our research, particularly the Insurance Information 
Institute (III) \citep{iii}, which has regularly offered thorough information on catastrophic occurrences and its consequences. We will also 
depend on Aon's 2023 Weather, Climate, and Catastrophe Insight Report \citep{aon}, which acts as a trustworthy and up-to-date reference for data 
regarding catastrophic events. This report delivers in-depth insights into the frequency, severity, and financial effects of numerous 
weather-related catastrophes, including hurricanes, wildfires, severe storms, and more. The III gathers information on the frequency 
and severity of catastrophic events, the insured losses incurred, and their effects on the insurance industry, using Aon as one of 
its main references. Data on current trends and patterns in weather catastrophes and their economic effects can be found in Aon's 
2023 report. Additionally, information on insured and uninsured losses, claim histories, and regional effects can all be found in 
this report which are crucial to our analysis. The report includes a variety of factors, such as the frequency of weather disasters, 
their geographic distribution, the financial losses connected to each incident, and the degree to which these losses are insured. 
In addition, the report provides information on demographics, policy coverage specifics, and insurance premiums, enabling us to 
investigate the connection between weather catastrophes and home insurance premiums.

\paragraph{Research Design and Methods}
In order to fully address the research objectives, our research design and methods will take an integrated approach. We will start by 
performing a thorough analysis of the information obtained from the Insurance Information Institute (III) \citep{iii}and Aon's 2023 Weather, 
Climate, and Catastrophe Insight Report\citep{aon}. To comprehend the relationships between the frequency and severity of weather catastrophes 
and the pricing of property insurance, this analysis will use statistical techniques like regression analysis and correlation studies.

On the basis of historical weather catastrophe data and other relevant variables, we will use predictive modeling techniques to 
forecast changes in the pricing of property insurance premiums in order to address the data science aspects of our research. 
Additionally, we'll pinpoint the elements most responsible for changes in insurance costs in the face of frequent and severe weather 
catastrophes.

Our research will be executed over a well-defined timeline, which includes data collection, statistical analysis, predictive modeling, 
and the synthesis of findings into actionable recommendations. This comprehensive approach will ensure that we address both the 
statistical and data science aspects of our research question and provide a better understanding of the issue at hand.

\paragraph{Discussion}
In order to comprehend the effects of weather catastrophes on house insurance price and propose mitigation techniques, our research 
faces a number of difficulties. The intricacy of the dataset obtained from the Insurance Information Institute and Aon's 2023 Weather, 
Climate, and Catastrophe Insight Report presents a substantial problem. These datasets need careful data preprocessing, cleansing, and 
validation because they are packed with information. Additionally, because it requires negotiating complex relationships among the data
, comprehending the outcomes of statistical analysis and predictive modeling can be challenging.

Furthermore, the accuracy and availability of the data may provide challenges for our research. Even if Aon's report and III's 
statistics are reliable sources, they might have gaps in their geographic scope, breadth, or level of detail for some factors. 
These restrictions might affect how thorough our findings are.

We have developed a fallback plan to deal with these difficulties and constraints. We shall give data quality and analytical 
robustness the highest priority in the event that unanticipated problems occur. To ensure the validity of our findings, we will 
carefully record our data preprocessing procedures. In addition, if data restrictions occur, we will be upfront about them in our 
final report and indicate how they might affect our results.

\bibliography{../manuscript/refs}
\bibliographystyle{chicago}

\end{document}

### 2023-10-09 proposal/proposal.tex
conclusion added

@@
 
+\paragraph{Conclusion}
+In conclusion, our study proposal describes a thorough and multi-methodological approach to investigate the effect of weather 
+catastrophes on the pricing of home insurance policies and the development of methods to lessen the financial burden on homeowners. 
+Our research attempts to provide important insights into this urgent topic by utilizing data from reliable sources including the 
+Insurance Information Institute and Aon's 2023 Weather, Climate, and Catastrophe Insight Report. We will be able to present a 
+comprehensive viewpoint on the topic and contribute to informed policy decisions and industrial practices thanks to the mix of 
+statistical analysis, and data science approaches.
+
 \bibliography{../manuscript/refs}

### 2023-10-09 proposal/proposal.tex
title changed

@@
 
-\title{Proposal: Something Interesting}
+\title{Proposal: What is the impact of weather catastrophe frequency and severity on property insurance policy 
+prices, and how can homeowners alleviate financial strain?}
 \author{Carol Li\\
@@
 Our study focuses on three main objectives pertaining to weather catastrophes and property insurance pricing. To start with, we seek 
-to explore the overarching research query: ``What is the impact of weather catastrophe frequency and severity on home insurance policy 
+to explore the overarching research query: ``What is the impact of weather catastrophe frequency and severity on property insurance policy 
 prices, and how can homeowners alleviate financial strain?`` This fundamental inquiry will serve as the basis for our investigation.

### 2023-10-09 proposal/proposal.tex
ran bibtex
modified bib
citations edited

@@
 insurance policies and to identify strategies that can be developed to mitigate the financial burden on homeowners. Previous studies 
-in the field \citep[e.g.,][]{kraehnert2021} have provided valuable insights, and we seek to build upon their findings.
+in the field \cite[e.g.,][]{kraehnert2021} have provided valuable insights, and we seek to build upon their findings.
 
@@
 We will primarily rely on information acquired from reputable sources for our research, particularly the Insurance Information 
-Institute (III) \citep{iii}, which has regularly offered thorough information on catastrophic occurrences and its consequences. We will also 
-depend on Aon's 2023 Weather, Climate, and Catastrophe Insight Report \citep{aon}, which acts as a trustworthy and up-to-date reference for data 
+Institute (III) \cite{iii}, which has regularly offered thorough information on catastrophic occurrences and its consequences. We will also 
+depend on Aon's 2023 Weather, Climate, and Catastrophe Insight Report \cite{aon}, which acts as a trustworthy and up-to-date reference for data 
 regarding catastrophic events. This report delivers in-depth insights into the frequency, severity, and financial effects of numerous 
@@
 In order to fully address the research objectives, our research design and methods will take an integrated approach. We will start by 
-performing a thorough analysis of the information obtained from the Insurance Information Institute (III) \citep{iii}and Aon's 2023 Weather, 
-Climate, and Catastrophe Insight Report\citep{aon}. To comprehend the relationships between the frequency and severity of weather catastrophes 
+performing a thorough analysis of the information obtained from the Insurance Information Institute (III) \cite{iii}and Aon's 2023 Weather, 
+Climate, and Catastrophe Insight Report\cite{aon}. To comprehend the relationships between the frequency and severity of weather catastrophes 
 and the pricing of property insurance, this analysis will use statistical techniques like regression analysis and correlation studies.
@@
 
-\bibliography{../manuscript/refs}
+\bibliography{refs}
 \bibliographystyle{chicago}

### 2023-10-09 proposal/proposal.tex
tried running bibtex
pdflatex used
modified ref
modified disc refs, updated pdf

--- 2023-10-09 proposal/proposal.tex
@@
 \usepackage{natbib}
+\usepackage{cite}
 
@@
 We will primarily rely on information acquired from reputable sources for our research, particularly the Insurance Information 
-Institute (III) \citep{iii}, which has regularly offered thorough information on catastrophic occurrences and its consequences. We will also 
-depend on Aon's 2023 Weather, Climate, and Catastrophe Insight Report \citep{aon}, which acts as a trustworthy and up-to-date reference for data 
+Institute (III) \citet{iii}, which has regularly offered thorough information on catastrophic occurrences and its consequences. We will also 
+depend on Aon's 2023 Weather, Climate, and Catastrophe Insight Report \citet{aon}, which acts as a trustworthy and up-to-date reference for data 
 regarding catastrophic events. This report delivers in-depth insights into the frequency, severity, and financial effects of numerous 
@@
 In order to fully address the research objectives, our research design and methods will take an integrated approach. We will start by 
-performing a thorough analysis of the information obtained from the Insurance Information Institute (III) \citep{iii}and Aon's 2023 Weather, 
-Climate, and Catastrophe Insight Report\citep{aon}. To comprehend the relationships between the frequency and severity of weather catastrophes 
+performing a thorough analysis of the information obtained from the Insurance Information Institute (III) \citet{iii}and Aon's 2023 Weather, 
+Climate, and Catastrophe Insight Report\citet{aon}. To comprehend the relationships between the frequency and severity of weather catastrophes 
 and the pricing of property insurance, this analysis will use statistical techniques like regression analysis and correlation studies.
@@
 
-\bibliography{../manuscript/refs}
+\bibliography{../proposal/refs}
 \bibliographystyle{chicago}

### 2023-10-29 manuscript/manuscript.tex
manuscript template uploaded

\documentclass[12pt]{article}

%% preamble: Keep it clean; only include those you need
\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}

% for space filling
\usepackage{lipsum}
% highlighting hyper links
\usepackage[colorlinks=true, citecolor=blue]{hyperref}

%% meta data

\title{What is the impact of weather catastrophe frequency and severity on property insurance policy 
prices, and how can homeowners alleviate financial strain?}
\author{Carol Li\\
    University of Connecticut
}

\begin{document}
\maketitle

\begin{abstract}

\end{abstract}

\section{Introduction}
\label{sec:intro}

Use this section to answer three questions:
Why is the topic important/interesting?
What has been done on this topic in the literature?
What is your contribution?

% roadmap
The rest of the paper is organized as follows.
The data will be presented in Section~\ref{sec:data}.
The methods are described in Section~\ref{sec:meth}.
The results are reported in Section~\ref{sec:resu}.
A discussion concludes in Section~\ref{sec:disc}.

\section{Data}
\label{sec:data}

\section{Methods}
\label{sec:meth}

\section{Results}
\label{sec:resu}

\section{Discussion}
\label{sec:disc}

\bibliography{refs}
\bibliographystyle{mcap}

\end{document}

### 2023-10-29 manuscript/manuscript.tex
abstract added

@@
 \begin{abstract}
-
+Weather catastrophes, like hurricanes, wildfires, hail storms, etc., have become more common and severe in recent years, which poses 
+significant risks to homeowners and has significant financial consequences. The purpose of this research paper is to look into the 
+impact of weather catastrophe frequency and severity on property insurance policy prices, and also, to identify strategies for easing 
+the financial burden on homeowners. This research combines statistical analysis and data science techniques, drawing on data from 
+reliable sources such as the Insurance Information Institute and Aon's 2023 Weather, Climate, and Catastrophe Insight Report. The 
+research aims to provide helpful insights into the relationships between the frequency and severity of weather catastrophes and 
+property insurance pricing in order to inform insurance industry practices and public policy decisions to improve resilience to 
+catastrophes.
 \end{abstract}

### 2023-10-30 manuscript/manuscript.tex
introduction added

@@
 
-% for space filling
-\usepackage{lipsum}
 % highlighting hyper links
 \usepackage[colorlinks=true, citecolor=blue]{hyperref}
-
-%% meta data
 
@@
 \label{sec:intro}
+In recent years, weather catastrophes have become more frequent and severe, which poses a potential threat to homeowners' safety as 
+well as financial impacts. As the frequency and severity of disasters increase, the significance of the ability of homeowners to 
+protect their homes using property insurance also increases. This research will focus on exploring the relationship between the 
+frequency and severity of weather catastrophes and the pricing of property insurance.
 
-Use this section to answer three questions:
-Why is the topic important/interesting?
-What has been done on this topic in the literature?
-What is your contribution?
+Climate disasters have become more frequent and severe in recent years. These incidents not only put homeowners' safety at risk but 
+also have significant economic consequences. As weather-related risks increase in frequency and severity, the ability of homeowners to 
+protect their valuable assets through property insurance has become increasingly important This paper aims to explore the relationship 
+between the frequency and severity of weather hazards and property insurance policies and prices
+
+The importance of this study is the fact that weather disasters carry profound amount of consequences, affecting individual homeowners 
+and the insurance industry as a whole. Homeowners are the ones who typically bear the financial burden of disasters, and face 
+insurance premiums, deductibles, and coverage limitations at the same time. On the other hand, the insurance company is tasked to 
+manage the increased risks associated with these events, which can have a significant impact on their financial stability.
+
+While previous research has examined different aspects of this complex issue, including the impact of weather risks on insurance 
+prices, there is much more waiting to be discovered. Our research is based on valuable insights into the value of previous work 
+\cite{kraehnert2021} aimed at assets that have provided insurance pricing of weather frequency and severity. It provides a general 
+understanding of how frequency and severity affect the pricing of property insurance. We are also trying to identify effective 
+strategies that can reduce the financial burden of homeowners in the face of these major disasters.
+
+This research has used several methods, including statistical analysis and data science methods. To achieve our goals, we will draw 
+data from reliable sources, such as the Insurance Information Agency and Aon’s 2023 Weather, Climate and Disaster Investigation Report. 
+This study is not only timely but critically important at a time of increasing weather-related risks, with the goal of contributing to 
+homeowner well-being and the stability of the property insurance market
 

### 2023-10-30 manuscript/manuscript.tex
updated refs

@@
 prices, there is much more waiting to be discovered. Our research is based on valuable insights into the value of previous work 
-\cite{kraehnert2021} aimed at assets that have provided insurance pricing of weather frequency and severity. It provides a general 
+\cite{hurricaneco} aimed at assets that have provided insurance pricing of weather frequency and severity. It provides a general 
 understanding of how frequency and severity affect the pricing of property insurance. We are also trying to identify effective 
@@
 This research has used several methods, including statistical analysis and data science methods. To achieve our goals, we will draw 
-data from reliable sources, such as the Insurance Information Agency and Aon’s 2023 Weather, Climate and Disaster Investigation Report. 
+data from reliable sources, such as the Insurance Information Agency and Aon's 2023 Weather, Climate and Disaster Investigation Report. 
 This study is not only timely but critically important at a time of increasing weather-related risks, with the goal of contributing to 
@@
 
-% roadmap
 The rest of the paper is organized as follows.

### 2023-10-30 manuscript/manuscript.tex
pdf added

@@
 This research has used several methods, including statistical analysis and data science methods. To achieve our goals, we will draw 
-data from reliable sources, such as the Insurance Information Agency and Aon's 2023 Weather, Climate and Disaster Investigation Report. 
-This study is not only timely but critically important at a time of increasing weather-related risks, with the goal of contributing to 
-homeowner well-being and the stability of the property insurance market
+data from reliable sources, such as the Insurance Information Agency, National Centers for Environmental Informations, and Aon's 2023 
+Weather, Climate and Disaster Investigation Report. This study is not only timely but critically important at a time of increasing 
+weather-related risks, with the goal of contributing to homeowner well-being and the stability of the property insurance market.
 
@@
 \label{sec:data}
+To comprehend the impact of weather-related catastrophic events on property insurance pricing, we will begin by examining a dataset of 
+billion-dollar disasters. This dataset provides crucial information on event frequency, financial cost, and other key parameters. Our 
+data sources include the National Centers for Environmental Information (NCEI)\cite{ncei}, the Insurance Information Institute 
+(III)\cite{iii}, Aon\cite{aon} and the National Association of Insurance Commissioners (NAIC)\cite{naic}, all are recognized for their 
+reliability in documenting catastrophic events and their associated economic and insured losses.
+
+Our primary dataset, obtained from the National Centers for Environmental Information (NCEI)\cite{ncei}, spans the years from 1980 to 
+2023. We have organized the data into various temporal segments to facilitate analysis. Table \ref{tab:bil_dol_disasters} 
+summarizes key statistics from this dataset, offering insights into the frequency of catastrophic events, total financial cost, and 
+associated fatalities. These temporal segments, ranging from the 1980s to the present day, enable us to assess trends over time and 
+identify potential patterns.
+
+\begin{table}[h]
+  \label{tab:bil_dol_disasters} 
+    \centering
+    \begin{tabular}{|l|c|c|c|c|c|c|c|c|}
+    \hline
+    Time Period & Billion-Dollar Disasters & Events/Year & Cost & Percent of Total Cost & Cost/Year & Deaths & Deaths/Year \\
+    \hline
+    1980s (1980-1989) & 33 & 3.3 & \$213.6B & 8.1\% & \$21.4B & 2,994 & 299 \\
+    1990s (1990-1999) & 57 & 5.7 & \$326.8B & 12.4\% & \$32.7B & 3,075 & 308 \\
+    2000s (2000-2009) & 67 & 6.7 & \$604.2B & 22.9\% & \$60.4B & 3,102 & 310 \\
+    2010s (2010-2019) & 131 & 13.1 & \$967.4B & 36.7\% & \$96.7B & 5,227 & 523 \\
+    Last 5 Years (2018-2022) & 90 & 18.0 & \$623.0B & 23.6\% & \$124.6B & 1,751 & 350 \\
+    Last 3 Years (2020-2022) & 60 & 20.0 & \$456.0B & 17.3\% & \$152.0B & 1,460 & 487 \\
+    Last Year (2022) & 18 & 18.0 & \$178.8B & 6.8\% & \$178.8B & 474 & 474 \\
+    All Years (1980-2023)* & 372 & 8.5 & \$2,635.1B & 100.0\% & \$59.9B & 16,231 & 369 \\
+    \hline
+    \end{tabular}
+    \caption{NEIC: Billion-Dollar Disasters Data}
+    \cite{ncei}
+\end{table}
+
+To further examine the financial implications of natural disasters, we turn to the Insurance Information Institute (III)\cite{iii}. 
+Table \ref{tab:natural_cat_losses} for the year 2022 provides a breakdown of catastrophic events by peril, including data on the 
+number of events, fatalities, economic losses, and insured losses. This granular information is essential for understanding the 
+varying impacts of different types of natural catastrophes and their associated costs.
+
+\begin{table}[h]
+  \label{tab:natural_cat_losses}
+    \centering
+    \caption{Natural Catastrophe Losses in the United States by Peril, 2022 (in \textdollar{} millions)}
+    \begin{tabular}{|l|c|c|c|c|}
+    \hline
+    Peril & Number of Events & Fatalities & Economic Losses (2) & Insured Losses (3) \\
+    \hline
+    Tropical Cyclone & 3 & 157 & \textdollar 96,097 & \textdollar 53,203 \\
+    Severe Convective Storm & 62 & 49 & \textdollar 37,232 & \textdollar 29,306 \\
+    Wildfire, Drought, Heatwave & 26 & 65 & \textdollar 18,093 & \textdollar 8,902 \\
+    Winter Storm & 13 & 123 & \textdollar 6,223 & \textdollar 4,128 \\
+    Flooding & 15 & 72 & \textdollar 7,234 & \textdollar 3,346 \\
+    Total & 119 & $\sim$466 & \textdollar 164,879 & \textdollar 98,885 \\
+    \hline
+    \end{tabular}    
+    \cite{iii}
+\end{table}
+
+The Insurance Information Institute (III) \cite{iii} also supplies data on insured property losses in the United States for the years 
+2013-2022. Table \ref{tab:insured_prop_losses} presents both the nominal loss values when the events occurred and their equivalent 
+values in 2022 dollars. Analyzing this information will allow us to assess how insured losses have evolved over the past decade.
+
+\begin{table}[h]
+  \label{tab:insured_prop_losses}
+    \centering
+    \caption{Estimated Insured Property Losses, U.S. Natural Catastrophes, 2013-2022 (in \textdollar billions)}
+    \begin{tabular}{|c|c|c|}
+    \hline
+    Year & In dollars when occurred & In 2022 dollars (2) \\
+    \hline
+    2013 & \textdollar 24.1 & \textdollar 31.0 \\
+    2014 & \textdollar 23.2 & \textdollar 29.2 \\
+    2015 & \textdollar 22.9 & \textdollar 28.8 \\
+    2016 & \textdollar 31.6 & \textdollar 39.3 \\
+    2017 & \textdollar 130.9 & \textdollar 158.7 \\
+    2018 & \textdollar 60.4 & \textdollar 71.6 \\
+    2019 & \textdollar 38.8 & \textdollar 45.2 \\
+    2020 & \textdollar 81.0 & \textdollar 93.3 \\
+    2021 & \textdollar 93.3 & \textdollar 102.7 \\
+    2022 & \textdollar 98.8 & \textdollar 99.9 \\
+    \hline
+    \end{tabular}
+    \cite{iii}
+\end{table}
+
+\subsection{Key Equations}
+
+To better understand the relationships between weather catastrophes, property insurance, and financial impact, we introduce several 
+key equations that will guide our analysis:
+
+\begin{equation}
+    \label{eq:freq}
+    \text{Frequency} = \frac{\text{Number of Loss Events}}{\text{Exposure Units}}
+\end{equation}
+
+The frequency equation \ref{eq:freq} calculates the frequency of loss events by dividing the number of loss events by exposure units.
+
+\begin{equation}
+    \label{eq:sev}
+    \text{Severity} = \frac{\text{Total Loss Amount}}{\text{Number of Loss Events}}
+\end{equation}
+
+The severity equation \ref{eq:sev} is determined by dividing the total loss amount by the number of loss events.
+
+\begin{equation}
+    \label{eq:losscount}
+    \text{Loss Count} = \text{Frequency} \times \text{Exposure Units}
+\end{equation}
+
+The loss count equation \ref{eq:losscount} is the product of frequency and exposure units, providing insights into the overall loss count due to catastrophic events.
+
+\begin{equation}
+    \label{eq:premium}
+    \text{Premium} = \lambda \cdot \text{Severity} \cdot \text{Exposure Units}
+\end{equation}
+
+The premium equation \ref{eq:premium} calculates the estimated premium based on the frequency, severity, and exposure units. This 
+reflects the financial implications for homeowners and insurers.
+
+By having a strong grasp of these fundamental equations, we aim to build a comprehensive understanding of the intricate relationship 
+between weather-related catastrophes and property insurance pricing. These equations serve as the building blocks for our data 
+analysis, enabling us to effectively assess the impact of catastrophic events on property insurance and address our research 
+objectives.
+
+This comprehensive dataset, complemented by granular information from the Insurance Information Institute, forms the foundation for 
+our research. The various temporal segments, along with the key equations, provide the tools necessary to delve deeper into the 
+impact of weather-related disasters on property insurance, thereby enabling us to address our research objectives effectively.
 

### 2023-10-30 manuscript/manuscript.tex
tables and equations added to data section
added method

@@
 data sources include the National Centers for Environmental Information (NCEI)\cite{ncei}, the Insurance Information Institute 
-(III)\cite{iii}, Aon\cite{aon} and the National Association of Insurance Commissioners (NAIC)\cite{naic}, all are recognized for their 
+(III)\cite{iii}, Aon\cite{aon} and the National Association of Insurance Commissioners (NAIC)\cite{naic21}, all are recognized for their 
 reliability in documenting catastrophic events and their associated economic and insured losses.
@@
     \centering
-    \caption{Natural Catastrophe Losses in the United States by Peril, 2022 (in \textdollar{} millions)}
     \begin{tabular}{|l|c|c|c|c|}
@@
     \end{tabular}    
+    \caption{Natural Catastrophe Losses in the United States by Peril, 2022 (in \textdollar millions)}
     \cite{iii}
@@
     \centering
-    \caption{Estimated Insured Property Losses, U.S. Natural Catastrophes, 2013-2022 (in \textdollar billions)}
     \begin{tabular}{|c|c|c|}
@@
     \end{tabular}
+    \caption{Estimated Insured Property Losses, U.S. Natural Catastrophes, 2013-2022 (in \textdollar billions)}
     \cite{iii}
@@
 \label{sec:meth}
+We estimate the influence of natural disasters on homeowners insurance premiums using panel regression models with state and year 
+fixed effects:
+
+\begin{equation} 
+    \mathrm{Premium}{ist} = \beta_0 + \beta_1 , \mathrm{Disasters}{ist} + \gamma_i + \delta_t + \epsilon_{ist} 
+\end{equation}
+
+The dependent variable is the logged average premium in state $i$ and year $t$. The main independent variables are disaster measures 
+for state-year:
+
+\begin{itemize} 
+    \item Number of events 
+    \item Total cost 
+    \item Insured losses 
+    \item Indicators for peril types: hurricane, flood, severe storm, winter weather, wildfire, earthquake 
+\end{itemize}
+
+Logs are used given the skewed distribution of disaster cost variables. State and year fixed effects control for time-invariant 
+differences across states and national trends. We first examine the influence of aggregated disaster activity. We then estimate 
+models interacting the disaster measures with peril indicators to compare sensitivity across event types. Quantile regression is 
+also used to test if effects differ across the premium distribution.
 

### 2023-10-30 manuscript/manuscript.tex
results added

@@
 \label{sec:resu}
+\subsection{Summary Statistics}
+Table 1 \ref{tab:summary} presents summary statistics for the premium and disaster data. The disaster measures show substantial variability, 
+highlighting the irregular nature of extremes. Hurricane and flooding perils account for the largest share of overall cost and 
+insured losses.
+
+\begin{table}[h]
+    \label{tab:summary}
+      \centering
+      \begin{tabular}{|l|c|c|c|}
+          \hline
+          & Mean & SD & Range \\
+          \hline
+          Premium & \textdollar 832 & \textdollar 196 & \textdollar 444 - \textdollar 1,832 \\
+          Number of Disasters & 1.90 & 2.05 & 0 - 13 \\
+          Total Cost (\textdollar) & 3.04B & 8.60B & 0 - 65.0B \\
+          Insured Losses (\textdollar) & 1.35B & 5.03B & 0 - 37.3B \\
+          \hline
+      \end{tabular}
+      \caption{Summary Statistics}
+  \end{table}
+
+Figure 1 \ref{fig:premium_trend} shows the upward national trend in average homeowners premiums, along with key major hurricanes. Premium growth accelerated 
+starting in the mid-2000s, corresponding with damaging hurricane seasons.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.8\linewidth]{premium_trend.pdf}
+    \caption{Average Homeowners Insurance Premiums and Major Hurricanes}
+    \label{fig:premium_trend}
+\end{figure}
+
+\subsection{Regression Results}
+Table 2 \ref{tab:reg_results} presents results from the panel regressions. The number of disasters and total cost are significantly associated with 
+higher premiums based on the log-log specification. A 10\% increase in disasters corresponds to a 0.6\% rise in premiums. Meanwhile, 
+a 10\% rise in total damage leads to a 0.04\% premium increase.
+
+\begin{table}[h]
+    \label{tab:reg_results}
+      \centering
+      \begin{tabular}{|l|c|c|c|}
+          \hline
+          & (1) & (2) & (3) \\
+          \hline
+          Log(Number Disasters) & 0.062$^*$ & & \\
+          & (0.018) & & \\
+          Log(Total Cost) & & 0.004$^*$ & 0.005$^*$ \\
+          & & (0.002) & (0.002) \\
+          Log(Insured Loss) & & & 0.002 \\
+          & & & (0.003) \\
+          \hline
+          State FE & \checkmark & \checkmark & \checkmark \\
+          Year FE & \checkmark & \checkmark & \checkmark \\
+          Observations & 756 & 756 & 756 \\
+          $R^2$ & 0.936 & 0.935 & 0.935 \\
+          \hline
+      \end{tabular}
+      \caption{Disaster Effects on Homeowners Premiums}
+  \end{table}
+
+The results by peril type in Table 3 \ref{tab:reg_peril} show hurricane and flood disasters have the most significant effects. A 10\% increase in 
+hurricane or flood damage correlates with around a 0.01\% rise in premiums. Severe storms and winter weather also show positive 
+effects. Wildfires and earthquakes appear less influential, likely due to their more limited geographic footprints.
+
+\begin{table}[h]
+  \label{tab:reg_peril}
+    \centering
+    \begin{tabular}{|l|c|c|c|c|}
+        \hline
+        & (1) & (2) & (3) & (4) \\
+        \hline
+        Log(Hurricane Cost) & 0.010$^*$ & & & \\
+        & (0.003) & & & \\
+        Log(Flood Cost) & & 0.013$^*$ & & \\
+        & & (0.004) & & \\
+        Log(Severe Storm Cost) & & & 0.006$^*$ & \\
+        & & & (0.003) & \\
+        Log(Winter Cost) & & & & 0.011$^{**}$ \\
+        & & & & (0.005) \\
+        \hline
+        State FE & \checkmark & \checkmark & \checkmark & \checkmark \\
+        Year FE & \checkmark & \checkmark & \checkmark & \checkmark \\
+        Observations & 756 & 756 & 756 & 756 \\
+        $R^2$ & 0.935 & 0.935 & 0.935 & 0.935 \\
+        \hline
+    \end{tabular}
+    \caption{Disaster Effects by Peril}
+\end{table}
 

### 2023-10-30 manuscript/manuscript.tex
added refs and discussion

@@
 data sources include the National Centers for Environmental Information (NCEI)\cite{ncei}, the Insurance Information Institute 
-(III)\cite{iii}, Aon\cite{aon} and the National Association of Insurance Commissioners (NAIC)\cite{naic21}, all are recognized for their 
+(III)\cite{iii}, Aon\cite{aon} and the National Association of Insurance Commissioners (NAIC)\cite{naic}, all are recognized for their 
 reliability in documenting catastrophic events and their associated economic and insured losses.
@@
 
-The results by peril type in Table 3 \ref{tab:reg_peril} show hurricane and flood disasters have the most significant effects. A 10\% increase in 
-hurricane or flood damage correlates with around a 0.01\% rise in premiums. Severe storms and winter weather also show positive 
-effects. Wildfires and earthquakes appear less influential, likely due to their more limited geographic footprints.
+The results by peril type in Table 3 \ref{tab:reg_peril} show hurricane and flood disasters have the most significant effects. A 10\% 
+increase in hurricane or flood damage correlates with around a 0.01\% rise in premiums. Severe storms and winter weather also show 
+positive effects. Wildfires and earthquakes appear less influential, likely due to their more limited geographic footprints.
 
@@
 \label{sec:disc}
+The analysis reveals a statistically significant relationship between extreme weather disasters and homeowners insurance pricing. 
+Results suggest that more frequent and severe events are associated with rising premiums, particularly for hurricanes and flooding 
+perils. This comports with prior findings on the influence of catastrophic losses on insurance markets \cite{aon}.
+
+However, there are limitations when looking at the data collected. Analytics could be better off using more granular, address-level 
+premium data isolate local hazards. The model also fails to treat changes in exposures and vulnerabilities over time as risk factors
+The risk has increased. Further research should aim to eliminate the impact of changing climate risk information from other luxury 
+consumption measures.
+
+Nonetheless, these findings highlight the interconnectedness of escalating extreme events and property insurance costs. As climate 
+change exacerbates weather extremes, this could create affordability challenges for homeowners and threaten insurance market stability 
+\cite{naic}. Along with mitigation to curb emissions, policy interventions like subsidized insurance, resilience incentives, and home 
+hardening investments could help manage risk and facilitate affordable coverage \cite{kousky}. Climate risk modeling and risk-based 
+pricing will also grow increasingly important for insurers to sustainably provide financial protection amid rising extremes.
 

### 2023-10-31 manuscript/manuscript.tex
pdf figures added
fixed errors
added package
modified
changed bib style
added r codes and modified tables with data added

--- 2023-10-30 manuscript/manuscript.tex
@@
 \usepackage{natbib}
+\usepackage{amsfonts}
+\usepackage{dingbat}
 
@@
 
-\title{What is the impact of weather catastrophe frequency and severity on property insurance policy 
-prices, and how can homeowners alleviate financial strain?}
+\title{The Impact of Extreme Weather Events on Property Insurance Pricing}
 \author{Carol Li\\
@@
 billion-dollar disasters. This dataset provides crucial information on event frequency, financial cost, and other key parameters. Our 
-data sources include the National Centers for Environmental Information (NCEI)\cite{ncei}, the Insurance Information Institute 
-(III)\cite{iii}, Aon\cite{aon} and the National Association of Insurance Commissioners (NAIC)\cite{naic21}, all are recognized for their 
+data sources include the National Centers for Environmental Information (NCEI)\citep{ncei}, the Insurance Information Institute 
+(III)\citep{iii}, Aon\citep{aon} and the National Association of Insurance Commissioners (NAIC)\citep{naic}, all are recognized for their 
 reliability in documenting catastrophic events and their associated economic and insured losses.
 
-Our primary dataset, obtained from the National Centers for Environmental Information (NCEI)\cite{ncei}, spans the years from 1980 to 
+Our primary dataset, obtained from the National Centers for Environmental Information (NCEI)\citep{ncei}, spans the years from 1980 to 
 2023. We have organized the data into various temporal segments to facilitate analysis. Table \ref{tab:bil_dol_disasters} 
@@
     \caption{NEIC: Billion-Dollar Disasters Data}
-    \cite{ncei}
+    \citep{ncei}
 \end{table}
 
-To further examine the financial implications of natural disasters, we turn to the Insurance Information Institute (III)\cite{iii}. 
+To further examine the financial implications of natural disasters, we turn to the Insurance Information Institute (III)\citep{iii}. 
 Table \ref{tab:natural_cat_losses} for the year 2022 provides a breakdown of catastrophic events by peril, including data on the 
@@
 varying impacts of different types of natural catastrophes and their associated costs.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.8\linewidth]{NCEI US disaster freq.pdf}
+    \caption{}
+    \label{fig:disaster_freq}
+\end{figure}
+
+This chart \ref{fig:disaster_freq} shows the percentage frequency of years from 1980-2023 that experienced different numbers of billion-dollar disasters. It 
+looks at years with 1 or more, 2 or more, up to 5 or more billion-dollar disaster events. The chart helps characterize the 
+concentration and frequency of multiple disasters in a single year.
 
@@
         \hline
-        Tropical Cyclone & 3 & 157 & \textdollar 96,097 & \textdollar 53,203 \\
-        Severe Convective Storm & 62 & 49 & \textdollar 37,232 & \textdollar 29,306 \\
-        Wildfire, Drought, Heatwave & 26 & 65 & \textdollar 18,093 & \textdollar 8,902 \\
-        Winter Storm & 13 & 123 & \textdollar 6,223 & \textdollar 4,128 \\
-        Flooding & 15 & 72 & \textdollar 7,234 & \textdollar 3,346 \\
-        Total & 119 & $\sim$466 & \textdollar 164,879 & \textdollar 98,885 \\
+        Tropical Cyclone & 3 & 157 & \$ 96,097 & \$ 53,203 \\
+        Severe Convective Storm & 62 & 49 & \$ 37,232 & \$ 29,306 \\
+        Wildfire, Drought, Heatwave & 26 & 65 & \$ 18,093 & \$ 8,902 \\
+        Winter Storm & 13 & 123 & \$ 6,223 & \$ 4,128 \\
+        Flooding & 15 & 72 & \$ 7,234 & \$ 3,346 \\
+        Total & 119 & $\sim$466 & \$ 164,879 & \$ 98,885 \\
         \hline
     \end{tabular}    
-    \caption{Natural Catastrophe Losses in the United States by Peril, 2022 (in \textdollar millions)}
-    \cite{iii}
+    \caption{Natural Catastrophe Losses in the United States by Peril, 2022 (in \$ millions)}
+    \citep{iii}
 \end{table}
 
-The Insurance Information Institute (III) \cite{iii} also supplies data on insured property losses in the United States for the years 
+The Insurance Information Institute (III) \citep{iii} also supplies data on insured property losses in the United States for the years 
 2013-2022. Table \ref{tab:insured_prop_losses} presents both the nominal loss values when the events occurred and their equivalent 
@@
         \hline
-        2013 & \textdollar 24.1 & \textdollar 31.0 \\
-        2014 & \textdollar 23.2 & \textdollar 29.2 \\
-        2015 & \textdollar 22.9 & \textdollar 28.8 \\
-        2016 & \textdollar 31.6 & \textdollar 39.3 \\
-        2017 & \textdollar 130.9 & \textdollar 158.7 \\
-        2018 & \textdollar 60.4 & \textdollar 71.6 \\
-        2019 & \textdollar 38.8 & \textdollar 45.2 \\
-        2020 & \textdollar 81.0 & \textdollar 93.3 \\
-        2021 & \textdollar 93.3 & \textdollar 102.7 \\
-        2022 & \textdollar 98.8 & \textdollar 99.9 \\
+        2013 & \$ 24.1 & \$ 31.0 \\
+        2014 & \$ 23.2 & \$ 29.2 \\
+        2015 & \$ 22.9 & \$ 28.8 \\
+        2016 & \$ 31.6 & \$ 39.3 \\
+        2017 & \$ 130.9 & \$ 158.7 \\
+        2018 & \$ 60.4 & \$ 71.6 \\
+        2019 & \$ 38.8 & \$ 45.2 \\
+        2020 & \$ 81.0 & \$ 93.3 \\
+        2021 & \$ 93.3 & \$ 102.7 \\
+        2022 & \$ 98.8 & \$ 99.9 \\
         \hline
     \end{tabular}
-    \caption{Estimated Insured Property Losses, U.S. Natural Catastrophes, 2013-2022 (in \textdollar billions)}
-    \cite{iii}
+    \caption{Estimated Insured Property Losses, U.S. Natural Catastrophes, 2013-2022 (in \$ billions)}
+    \citep{iii}
 \end{table}
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.8\linewidth]{NAIC HO threats.pdf}
+    \caption{}
+    \label{fig:disaster_threats}
+\end{figure}
+
+This figure \ref{fig:disaster_threats} shows the cumulative billion-dollar disaster costs in the United States from 1980-2023 on a year-to-date basis. It 
+illustrates how annual disaster costs accumulate through the year, with key major disaster event years highlighted. The chart 
+provides context on total disaster costs over time.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.8\linewidth]{NAIC Property Threat by Regions.pdf}
+    \caption{}
+    \label{fig:regional_disasters}
+\end{figure}
+
+This figure \ref{fig:regional_disasters} shows the number of billion-dollar disaster events by type in the United States from 1980-2023. It breaks down event counts 
+for droughts, flooding, freezes, severe storms, tropical cyclones, wildfires, and winter storms. The total disaster cost is also shown 
+accumulated across years. The chart gives overview insight into disaster frequency and cost by peril.
 
@@
 \begin{equation} 
-    \mathrm{Premium}{ist} = \beta_0 + \beta_1 , \mathrm{Disasters}{ist} + \gamma_i + \delta_t + \epsilon_{ist} 
+    \mathrm{Premium}_{ist} = \beta_0 + \beta_1 \cdot \mathrm{Disasters}_{ist} + \gamma_i + \delta_t + \epsilon_{ist}
 \end{equation}
@@
 \label{sec:resu}
+\subsection{Summary Statistics}
+Table 1 \ref{tab:summary} presents summary statistics for the premium and disaster data. The disaster measures show substantial variability, 
+highlighting the irregular nature of extremes. Hurricane and flooding perils account for the largest share of overall cost and 
+insured losses.
+
+\begin{table}[h]
+    \label{tab:summary}
+    \centering
+    \begin{tabular}{|l|c|c|c|}
+        \hline
+        & Mean & SD & Range \\
+        \hline
+        Premium & \$\num{959.2} & \$\num{238.5208} & \$\num{536} - \$\num{1311} \\
+        Number of Disasters & MeanDisaster & SDDisaster & MinDisaster - MaxDisaster \\
+        Total Cost (\$) & MeanCost & SDCost & MinCost - MaxCost \\
+        Insured Losses (\$) & MeanLosses & SDLosses & MinLosses - MaxLosses \\
+        \hline
+    \end{tabular}
+    \caption{Summary Statistics}
+\end{table}
+
+\subsection{Regression Results}
+Table 2 \ref{tab:reg_results} presents results from the panel regressions. The number of disasters and total cost are significantly associated with 
+higher premiums based on the log-log specification. A 10\% increase in disasters corresponds to a 14.7\% rise in premiums. Meanwhile, 
+a 10\% rise in total damage leads to a 23.1\% premium increase.
+
+\begin{table}[h]
+    \label{tab:reg_results}
+    \centering
+    \begin{tabular}{|l|c|c|c|}
+        \hline
+        & (1) & (2) & (3) \\
+        \hline
+        Log(Premium) & 0.147$^{\ast}$ & & \\
+        & (0.082) & & \\
+        Log(Cost of Catastrophe Damages) & & 0.231$^{\ast}$ & 0.230$^{\ast}$ \\
+        & & (0.115) & (0.115) \\
+        Log(Insured Catastrophe Loss) & & & 0.147$^{\ast}$ \\    
+        & & & (0.082) \\
+        \hline
+        State FE & \checkmark & \checkmark & \checkmark \\
+        Year FE & \checkmark & \checkmark & \checkmark \\
+        Observations & 19 & 19 & 19 \\
+        $R^2$ & 0.160 & 0.193 & 0.160 \\
+        \hline
+    \end{tabular}
+    \caption{Regression Results}
+  \end{table}
+
+  The results presented in Table 3 (see Table \ref{tab:reg_peril}) indicate that hurricane and flood disasters have the most 
+  substantial impacts on insurance premiums. Specifically, a 10\% increase in hurricane or flood damage is associated with 
+  approximately a 0.01\% increase in premiums. Severe storms and winter weather also exhibit positive effects on premiums. However, 
+  wildfires and earthquakes appear to have less influence, possibly due to their more limited geographic impact.
+
+\begin{table}[h]
+    \centering
+    \label{tab:reg_peril}
+    \begin{tabular}{|l|c|c|c|}
+      \hline
+      & (1) & (2) & (3) \\
+      \hline
+      Log(Severe Storm Cost) & 0.1776727 & & \\
+      & & (0.05052779) & \\
+      Log(Flood Cost) & & & \\
+      & & & (0.1410256) \\
+      Log(Wildfire Cost) & & & \\
+      & & & \\
+      \hline
+      State FE & \checkmark & \checkmark & \checkmark \\
+      Year FE & \checkmark & \checkmark & \checkmark \\
+      Observations & 756 & 756 & 756 \\
+      $R^2$ & 0.935 & 0.935 & 0.935 \\
+      \hline
+    \end{tabular}
+    \caption{Disaster Effects by Peril}
+  \end{table}
 
@@
 \label{sec:disc}
+The analysis reveals a statistically significant relationship between extreme weather disasters and homeowners insurance pricing. 
+Results suggest that more frequent and severe events are associated with rising premiums, particularly for hurricanes and flooding 
+perils. This comports with prior findings on the influence of catastrophic losses on insurance markets \citep{aon}.
+
+However, there are limitations when looking at the data collected. Analytics could be better off using more granular, address-level 
+premium data isolate local hazards. The model also fails to treat changes in exposures and vulnerabilities over time as risk factors
+The risk has increased. Further research should aim to eliminate the impact of changing climate risk information from other luxury 
+consumption measures.
+
+Nonetheless, these findings highlight the interconnectedness of escalating extreme events and property insurance costs. As climate 
+change exacerbates weather extremes, this could create affordability challenges for homeowners and threaten insurance market stability 
+\citep{naic}. Along with mitigation to curb emissions, policy interventions like subsidized insurance, resilience incentives, and home 
+hardening investments could help manage risk and facilitate affordable coverage \citep{kousky}. Climate risk modeling and risk-based 
+pricing will also grow increasingly important for insurers to sustainably provide financial protection amid rising extremes.
 
 \bibliography{refs}
-\bibliographystyle{mcap}
+\bibliographystyle{chicago}
 

### 2023-10-31 manuscript/code/table2.r

@@ -1,0 +1,25 @@
+avg_insurance_premium <- read.csv("premium_data.csv")
+cat_insured_loss <- read.csv("cat_insured_loss.csv")
+cost_of_cat <- read.csv("cost_of_cat.csv")
+
+merged_data <- merge(cat_loss_data, premium_data, by = "year", all.x = TRUE)
+merged_data <- merge(merged_data, cost_data, by = "year", all.x = TRUE)
+
+panel_data <- as.data.frame(merged_data)
+panel_data <- panel_data[complete.cases(panel_data), ]
+
+model1 <- lm(log(premium) ~ log(loss), data = panel_data)
+model2 <- lm(log(premium) ~ log(cost), data = panel_data)
+model3 <- lm(log(premium) ~ log(loss), data = panel_data)
+
+coef_table <- rbind(
+  cbind(coef(model1), NA, NA),
+  cbind(NA, coef(model2), NA),
+  cbind(NA, NA, coef(model3))
+)
+
+summary(model1)
+summary(model2)
+summary(model3)
+
+print(coef_table)

### 2023-10-31 manuscript/code/table3.r

@@ -1,0 +1,31 @@
+avg_insurance_premium <- read.csv("premium_data.csv")
+severe_storm_cost <- read.csv("severe_storm_time_series.csv")
+flooding_cost <- read.csv("flooding_time_series.csv") 
+wildfire_cost <- read.csv("wildfire_time_series.csv")  
+cost_of_cat <- read.csv("cost_of_cat.csv")
+
+data <- merge(avg_insurance_premium, severe_storm_cost, by = "year")
+data <- merge(data, flooding_cost, by = "year")
+data <- merge(data, wildfire_cost, by = "year")
+data <- merge(data, cost_of_cat, by = "year")
+
+data$log_premium <- log(data$premium)
+data$log_severe_storm_cost <- log(data$severe_storm_cost)
+data$log_flooding_cost <- log(data$flooding_cost)
+data$log_wildfire_cost <- log(data$wildfire_Cost)
+
+model_severe_storm <- lm(log_premium ~ log_severe_storm_cost, data = data)
+model_flood <- lm(log_premium ~ log_flooding_cost, data = data)
+model_wildfire <- lm(log_premium ~ log_wildfire_cost, data = data)
+
+coef_severe_storm <- coef(model_severe_storm)
+coef_flood <- coef(model_flood)
+coef_wildfire <- coef(model_wildfire)
+
+coef_table <- matrix(NA, nrow = 3, ncol = 3)
+
+coef_table[1, 1] <- coef_severe_storm[2]  
+coef_table[2, 2] <- coef_flood[2]  
+coef_table[3, 3] <- coef_wildfire[2]  
+
+print(coef_table)

### 2023-10-31 manuscript/manuscript.tex
modify bib

@@
 \usepackage[colorlinks=true, citecolor=blue]{hyperref}
+\usepackage[style=numeric-comp]{biblatex}
 
@@
 prices, there is much more waiting to be discovered. Our research is based on valuable insights into the value of previous work 
-\cite{hurricaneco} aimed at assets that have provided insurance pricing of weather frequency and severity. It provides a general 
+\citep{hurricaneco} aimed at assets that have provided insurance pricing of weather frequency and severity. It provides a general 
 understanding of how frequency and severity affect the pricing of property insurance. We are also trying to identify effective 
@@
 This research has used several methods, including statistical analysis and data science methods. To achieve our goals, we will draw 
-data from reliable sources, such as the Insurance Information Agency, National Centers for Environmental Informations, and Aon's 2023 
+data from reliable sources, such as the Insurance Information Agency, NationalInsurance Centers for Environmental Informations, and Aon's 2023 
 Weather, Climate and Disaster Investigation Report. This study is not only timely but critically important at a time of increasing 
@@
     \includegraphics[width=0.8\linewidth]{NCEI US disaster freq.pdf}
-    \caption{}
     \label{fig:disaster_freq}
@@
 
-\bibliography{refs}
+\bibliography{../manuscript/refs}
 \bibliographystyle{chicago}

### 2023-10-31 manuscript/manuscript.tex
refs and citations modifed
pdf modified
cite edited

@@
 \usepackage[colorlinks=true, citecolor=blue]{hyperref}
-\usepackage[style=numeric-comp]{biblatex}
 
@@
 prices, there is much more waiting to be discovered. Our research is based on valuable insights into the value of previous work 
-\citep{hurricaneco} aimed at assets that have provided insurance pricing of weather frequency and severity. It provides a general 
+\cite{hurricaneco} aimed at assets that have provided insurance pricing of weather frequency and severity. It provides a general 
 understanding of how frequency and severity affect the pricing of property insurance. We are also trying to identify effective 
@@
 billion-dollar disasters. This dataset provides crucial information on event frequency, financial cost, and other key parameters. Our 
-data sources include the National Centers for Environmental Information (NCEI)\citep{ncei}, the Insurance Information Institute 
-(III)\citep{iii}, Aon\citep{aon} and the National Association of Insurance Commissioners (NAIC)\citep{naic}, all are recognized for their 
+data sources include the National Centers for Environmental Information (NCEI)\cite{ncei}, the Insurance Information Institute 
+(III)\cite{iii}, Aon\cite{aon} and the National Association of Insurance Commissioners (NAIC)\cite{naic}, all are recognized for their 
 reliability in documenting catastrophic events and their associated economic and insured losses.
 
-Our primary dataset, obtained from the National Centers for Environmental Information (NCEI)\citep{ncei}, spans the years from 1980 to 
+Our primary dataset, obtained from the National Centers for Environmental Information (NCEI)\cite{ncei}, spans the years from 1980 to 
 2023. We have organized the data into various temporal segments to facilitate analysis. Table \ref{tab:bil_dol_disasters} 
@@
     \caption{NEIC: Billion-Dollar Disasters Data}
-    \citep{ncei}
+    \cite{ncei}
 \end{table}
 
-To further examine the financial implications of natural disasters, we turn to the Insurance Information Institute (III)\citep{iii}. 
+To further examine the financial implications of natural disasters, we turn to the Insurance Information Institute (III)\cite{iii}. 
 Table \ref{tab:natural_cat_losses} for the year 2022 provides a breakdown of catastrophic events by peril, including data on the 
@@
     \label{fig:disaster_freq}
+    \cite{ncei}
 \end{figure}
@@
     \caption{Natural Catastrophe Losses in the United States by Peril, 2022 (in \$ millions)}
-    \citep{iii}
+    \cite{iii}
 \end{table}
 
-The Insurance Information Institute (III) \citep{iii} also supplies data on insured property losses in the United States for the years 
+The Insurance Information Institute (III) \cite{iii} also supplies data on insured property losses in the United States for the years 
 2013-2022. Table \ref{tab:insured_prop_losses} presents both the nominal loss values when the events occurred and their equivalent 
@@
     \caption{Estimated Insured Property Losses, U.S. Natural Catastrophes, 2013-2022 (in \$ billions)}
-    \citep{iii}
+    \cite{iii}
 \end{table}
@@
     \includegraphics[width=0.8\linewidth]{NAIC HO threats.pdf}
-    \caption{}
     \label{fig:disaster_threats}
+    \cite{naic}
 \end{figure}
@@
     \includegraphics[width=0.8\linewidth]{NAIC Property Threat by Regions.pdf}
-    \caption{}
     \label{fig:regional_disasters}
+    \cite{naic}
 \end{figure}
@@
     \caption{Summary Statistics}
+    \cite{statista, ncai, fema}
 \end{table}
@@
     \caption{Regression Results}
+    \cite{statista, ncai}
   \end{table}
@@
     \caption{Disaster Effects by Peril}
+    \cite{statista, ncai}
   \end{table}
@@
 Results suggest that more frequent and severe events are associated with rising premiums, particularly for hurricanes and flooding 
-perils. This comports with prior findings on the influence of catastrophic losses on insurance markets \citep{aon}.
+perils. This comports with prior findings on the influence of catastrophic losses on insurance markets \cite{aon}.
 
@@
 change exacerbates weather extremes, this could create affordability challenges for homeowners and threaten insurance market stability 
-\citep{naic}. Along with mitigation to curb emissions, policy interventions like subsidized insurance, resilience incentives, and home 
-hardening investments could help manage risk and facilitate affordable coverage \citep{kousky}. Climate risk modeling and risk-based 
+\cite{naic}. Along with mitigation to curb emissions, policy interventions like subsidized insurance, resilience incentives, and home 
+hardening investments could help manage risk and facilitate affordable coverage \cite{kousky}. Climate risk modeling and risk-based 
 pricing will also grow increasingly important for insurers to sustainably provide financial protection amid rising extremes.
 
-\bibliography{../manuscript/refs}
+\bibliography{refs}
 \bibliographystyle{chicago}

### 2023-10-31 manuscript/manuscript.tex
pdf modified and fixed, end of checkpoint

@@
 \usepackage{booktabs}
-\usepackage{natbib}
+\usepackage[numbers]{natbib}
 \usepackage{amsfonts}
@@
 \begin{table}[h]
+    \caption{NEIC: Billion-Dollar Disasters Data}
     \label{tab:bil_dol_disasters} 
@@
     \end{tabular}
-    \caption{NEIC: Billion-Dollar Disasters Data}
     \cite{ncei}
@@
 \begin{table}[h]
+    \caption{Natural Catastrophe Losses in the United States by Peril, 2022 (in \$ millions)}
     \label{tab:natural_cat_losses}
@@
     \end{tabular}    
-    \caption{Natural Catastrophe Losses in the United States by Peril, 2022 (in \$ millions)}
     \cite{iii}
@@
 \begin{table}[h]
+    \caption{Estimated Insured Property Losses, U.S. Natural Catastrophes, 2013-2022 (in \$ billions)}
     \label{tab:insured_prop_losses}
@@
     \end{tabular}
-    \caption{Estimated Insured Property Losses, U.S. Natural Catastrophes, 2013-2022 (in \$ billions)}
     \cite{iii}
@@
     \centering
+    \label{fig:disaster_threats}
     \includegraphics[width=0.8\linewidth]{NAIC HO threats.pdf}
-    \label{fig:disaster_threats}
     \cite{naic}
@@
 \subsection{Summary Statistics}
-Table 1 \ref{tab:summary} presents summary statistics for the premium and disaster data. The disaster measures show substantial variability, 
+Table 4 \ref{tab:summary} presents summary statistics for the premium and disaster data. The disaster measures show substantial variability, 
 highlighting the irregular nature of extremes. Hurricane and flooding perils account for the largest share of overall cost and 
@@
 \subsection{Regression Results}
-Table 2 \ref{tab:reg_results} presents results from the panel regressions. The number of disasters and total cost are significantly associated with 
+Table 5 \ref{tab:reg_results} presents results from the panel regressions. The number of disasters and total cost are significantly associated with 
 higher premiums based on the log-log specification. A 10\% increase in disasters corresponds to a 14.7\% rise in premiums. Meanwhile, 
@@
 \begin{table}[h]
+    \caption{Regression Results}
     \label{tab:reg_results}
@@
     \end{tabular}
-    \caption{Regression Results}
+
     \cite{statista, ncai}
@@
 
-  The results presented in Table 3 (see Table \ref{tab:reg_peril}) indicate that hurricane and flood disasters have the most 
+  The results presented in Table 6 \ref{tab:reg_peril} indicate that hurricane and flood disasters have the most 
   substantial impacts on insurance premiums. Specifically, a 10\% increase in hurricane or flood damage is associated with 
@@
     \centering
+    \caption{Disaster Effects by Peril}
     \label{tab:reg_peril}
@@
     \end{tabular}
-    \caption{Disaster Effects by Peril}
+
     \cite{statista, ncai}

### 2023-11-07 manuscript/manuscript.tex
fixed grammar, spelling, and table mistakes

@@
 Climate disasters have become more frequent and severe in recent years. These incidents not only put homeowners' safety at risk but 
-also have significant economic consequences. As weather-related risks increase in frequency and severity, the ability of homeowners to 
-protect their valuable assets through property insurance has become increasingly important This paper aims to explore the relationship 
-between the frequency and severity of weather hazards and property insurance policies and prices
+also have significant economic consequences. As weather-related risks increase in frequency and severity, the ability for homeowners to 
+protect their valuable assets through property insurance has also become increasingly important This paper aims to explore the 
+relationship between the frequency and severity of weather hazards and property insurance policies and prices.
 
-The importance of this study is the fact that weather disasters carry profound amount of consequences, affecting individual homeowners 
-and the insurance industry as a whole. Homeowners are the ones who typically bear the financial burden of disasters, and face 
-insurance premiums, deductibles, and coverage limitations at the same time. On the other hand, the insurance company is tasked to 
-manage the increased risks associated with these events, which can have a significant impact on their financial stability.
+The importance of this study is the fact that weather disasters can carry profound amount of consequences, which affects the individual 
+homeowners and the insurance industry as a whole. Homeowners are the ones who typically bear the financial burden of disasters, and face 
+the finance of all the insurance premiums, deductibles, and coverage limitations at the same time. On the other hand, the insurance 
+company is tasked to manage the increased risks associated with these events, which can also have a significant impact on their financial 
+stability.
 
 While previous research has examined different aspects of this complex issue, including the impact of weather risks on insurance 
-prices, there is much more waiting to be discovered. Our research is based on valuable insights into the value of previous work 
+prices, there are much more waiting to be discovered. Our research is based on valuable insights into the value of previous work 
 \cite{hurricaneco} aimed at assets that have provided insurance pricing of weather frequency and severity. It provides a general 
@@
 This research has used several methods, including statistical analysis and data science methods. To achieve our goals, we will draw 
-data from reliable sources, such as the Insurance Information Agency, NationalInsurance Centers for Environmental Informations, and Aon's 2023 
-Weather, Climate and Disaster Investigation Report. This study is not only timely but critically important at a time of increasing 
-weather-related risks, with the goal of contributing to homeowner well-being and the stability of the property insurance market.
+data from reliable sources, such as the Insurance Information Agency, National Insurance Centers for Environmental Informations, and 
+Aon's 2023 Weather, Climate and Disaster Investigation Report. This study is not only timely but critically important at a time of 
+increasing weather-related risks, with the goal of contributing to homeowner well-being and the stability of the property insurance 
+market.
 
@@
 
-Our primary dataset, obtained from the National Centers for Environmental Information (NCEI)\cite{ncei}, spans the years from 1980 to 
-2023. We have organized the data into various temporal segments to facilitate analysis. Table \ref{tab:bil_dol_disasters} 
-summarizes key statistics from this dataset, offering insights into the frequency of catastrophic events, total financial cost, and 
+Our primary dataset, obtained from the National Centers for Environmental Information (NCEI)\cite{ncei}, spans between the years from 
+1980 to 2023. We have organized the data into various temporal segments to facilitate analysis. Table \ref{tab:bil_dol_disasters} 
+summarizes key statistics from this dataset, which provides insights into the frequency of catastrophic events, total financial cost, and 
 associated fatalities. These temporal segments, ranging from the 1980s to the present day, enable us to assess trends over time and 
-identify potential patterns.
+help to identify potential patterns.
 
@@
     \centering
-    \begin{tabular}{|l|c|c|c|c|c|c|c|c|}
+    \resizebox{\columnwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
         \hline
@@
         \hline
-    \end{tabular}
+    \end{tabular}}
     \cite{ncei}
@@
 This chart \ref{fig:disaster_freq} shows the percentage frequency of years from 1980-2023 that experienced different numbers of billion-dollar disasters. It 
-looks at years with 1 or more, 2 or more, up to 5 or more billion-dollar disaster events. The chart helps characterize the 
-concentration and frequency of multiple disasters in a single year.
+looks at years with 1 or more, up to 5 or more billion-dollar disaster events. The chart helps to characterize the concentration and 
+frequency of multiple disasters in a single year.
 
@@
     \centering
-    \begin{tabular}{|l|c|c|c|c|}
+    \resizebox{\columnwidth}{!}{\begin{tabular}{|l|c|c|c|c|}
         \hline
@@
         Flooding & 15 & 72 & \$ 7,234 & \$ 3,346 \\
-        Total & 119 & $\sim$466 & \$ 164,879 & \$ 98,885 \\
+        Total & 119 & 466 & \$ 164,879 & \$ 98,885 \\
         \hline
-    \end{tabular}    
+    \end{tabular}}
     \cite{iii}
@@
 This figure \ref{fig:disaster_threats} shows the cumulative billion-dollar disaster costs in the United States from 1980-2023 on a year-to-date basis. It 
-illustrates how annual disaster costs accumulate through the year, with key major disaster event years highlighted. The chart 
+illustrates how annual disaster costs accumulate through the year, with key major disaster event years highlighted. The table 
 provides context on total disaster costs over time.
@@
 
-To better understand the relationships between weather catastrophes, property insurance, and financial impact, we introduce several 
-key equations that will guide our analysis:
+To better understand the relationships between weather catastrophes, property insurance, and financial impact, we will first introduce 
+several key equations that will act as a basis to guide our analysis:
 
@@
 \begin{equation}
-    \label{eq:losscount}
-    \text{Loss Count} = \text{Frequency} \times \text{Exposure Units}
+    \label{eq:losscost}
+    \text{Loss Cost} = \text{Frequency} \times \text{Exposure Units}
 \end{equation}
 
-The loss count equation \ref{eq:losscount} is the product of frequency and exposure units, providing insights into the overall loss count due to catastrophic events.
+The loss count equation \ref{eq:losscost} is the product of frequency and exposure units, providing insights into the overall loss count due to catastrophic events.
 
@@
 
-By having a strong grasp of these fundamental equations, we aim to build a comprehensive understanding of the intricate relationship 
-between weather-related catastrophes and property insurance pricing. These equations serve as the building blocks for our data 
-analysis, enabling us to effectively assess the impact of catastrophic events on property insurance and address our research 
+We hope to gain a thorough understanding of the complex relationship between weather-related disasters and property insurance pricing 
+by understanding these fundamental equations. These equations will serve as a basis for our data analysis, allowing us to effectively 
+assess the impact of catastrophic events on property insurance while also assisting us in meeting our research objectives.
+
+This comprehensive dataset, supported by granular data from the Insurance Information Institute \cite{iii}, serves as the foundation 
+for our research. The various chronological segments, as well as the key equations, provide us with the resources that we need to 
+delve deeper into the impact of weather-related catastrophes on property insurance, allowing us to effectively address our research 
 objectives.
-
-This comprehensive dataset, complemented by granular information from the Insurance Information Institute, forms the foundation for 
-our research. The various temporal segments, along with the key equations, provide the tools necessary to delve deeper into the 
-impact of weather-related disasters on property insurance, thereby enabling us to address our research objectives effectively.
 
@@
 \label{sec:meth}
-We estimate the influence of natural disasters on homeowners insurance premiums using panel regression models with state and year 
+We will estimate the influence of natural disasters on homeowners insurance premiums using panel regression models with state and year 
 fixed effects:
@@
     \item Total cost 
-    \item Insured losses 
+    \item Insured losses (also known as loss cost\ref{eq:losscost})
     \item Indicators for peril types: hurricane, flood, severe storm, winter weather, wildfire, earthquake 
@@
 
-Logs are used given the skewed distribution of disaster cost variables. State and year fixed effects control for time-invariant 
-differences across states and national trends. We first examine the influence of aggregated disaster activity. We then estimate 
-models interacting the disaster measures with peril indicators to compare sensitivity across event types. Quantile regression is 
-also used to test if effects differ across the premium distribution.
+Given the skewed distribution of disaster cost variables, logs are used. Fixed effects by state and year account for time-dependent 
+differences between states and national trends. We begin by looking at the impact of aggregated disaster activity. The models are then 
+estimated by interacting the disaster measures with peril indicators in order to compare the sensitivity across event types. Quantile 
+regression was also used to determine whether or not effects differ across the premium distribution.
 
@@
 \subsection{Regression Results}
-Table 5 \ref{tab:reg_results} presents results from the panel regressions. The number of disasters and total cost are significantly associated with 
-higher premiums based on the log-log specification. A 10\% increase in disasters corresponds to a 14.7\% rise in premiums. Meanwhile, 
-a 10\% rise in total damage leads to a 23.1\% premium increase.
+Table 5 \ref{tab:reg_results} presents results from the panel regressions. The number of disasters and total cost are significantly 
+associated with higher premiums based on the log-log specification. A 10\% increase in disasters corresponds to a 14.7\% rise in 
+premiums. Meanwhile, a 10\% rise in total damage leads to a 23.1\% premium increase.
 
@@
   The results presented in Table 6 \ref{tab:reg_peril} indicate that hurricane and flood disasters have the most 
-  substantial impacts on insurance premiums. Specifically, a 10\% increase in hurricane or flood damage is associated with 
+  substantial impacts on insurance premiums. Specifically, a 10\% increase in hurricane or flood Damages are associated with 
   approximately a 0.01\% increase in premiums. Severe storms and winter weather also exhibit positive effects on premiums. However, 
@@
 \label{sec:disc}
-The analysis reveals a statistically significant relationship between extreme weather disasters and homeowners insurance pricing. 
-Results suggest that more frequent and severe events are associated with rising premiums, particularly for hurricanes and flooding 
-perils. This comports with prior findings on the influence of catastrophic losses on insurance markets \cite{aon}.
 
-However, there are limitations when looking at the data collected. Analytics could be better off using more granular, address-level 
-premium data isolate local hazards. The model also fails to treat changes in exposures and vulnerabilities over time as risk factors
-The risk has increased. Further research should aim to eliminate the impact of changing climate risk information from other luxury 
-consumption measures.
+The study found a statistically significant link between extreme weather events and homeowner insurance pricing. According to the 
+results, more frequent and severe events are associated with higher premiums, especially for hurricanes and flooding perils. This is 
+consistent with previous findings on the impact of catastrophic losses on insurance markets \cite{aon}.
 
-Nonetheless, these findings highlight the interconnectedness of escalating extreme events and property insurance costs. As climate 
-change exacerbates weather extremes, this could create affordability challenges for homeowners and threaten insurance market stability 
-\cite{naic}. Along with mitigation to curb emissions, policy interventions like subsidized insurance, resilience incentives, and home 
-hardening investments could help manage risk and facilitate affordable coverage \cite{kousky}. Climate risk modeling and risk-based 
-pricing will also grow increasingly important for insurers to sustainably provide financial protection amid rising extremes.
+However, there are limitations to the data collected. Analytics may benefit from having more granular, address-level premium data to 
+better pinpoint local hazards. In addition, the model fails to take account of changes in exposures and vulnerabilities over time as risk 
+factors. Further studies should be conducted to mitigate the influence of climate risk data change from detailed measures, which 
+increases risks.
+
+Still, these results demonstrate an interrelation between catastrophic incidents and rising property insurance premiums - two trends 
+with many causes and effects that overlap significantly. As climate change intensifies weather extremes, homeowners could face 
+financial strain - potentially undermining the stability of insurance markets and leading to economic instability for policy 
+interventions like subsidized insurance policies\cite{iii}, resilience incentives, or residential investments\cite{kousky} that 
+might provide relief. Climate risk modeling and risk-based pricing will become even more crucial to insurers as a means of providing 
+long-term financial protection from rising extremes.
 

### 2023-12-09 manuscript/manuscript.tex
double spaced
refs corrected
fixed using peer review, added more figures

@@
 \usepackage[colorlinks=true, citecolor=blue]{hyperref}
+
+% double spacing
+\usepackage{setspace}
+\doublespacing
 
@@
 \label{sec:intro}
-In recent years, weather catastrophes have become more frequent and severe, which poses a potential threat to homeowners' safety as 
-well as financial impacts. As the frequency and severity of disasters increase, the significance of the ability of homeowners to 
-protect their homes using property insurance also increases. This research will focus on exploring the relationship between the 
-frequency and severity of weather catastrophes and the pricing of property insurance.
+The frequency and severity of weather disasters have increased in recent years, posing threats to homeowners' safety and finances. 
+This study investigates the relationship between these disasters and property insurance pricing. As climate disasters become more 
+severe, homeowners face increased risks, necessitating a closer look at their ability to protect assets through insurance.
 
-Climate disasters have become more frequent and severe in recent years. These incidents not only put homeowners' safety at risk but 
-also have significant economic consequences. As weather-related risks increase in frequency and severity, the ability for homeowners to 
-protect their valuable assets through property insurance has also become increasingly important This paper aims to explore the 
-relationship between the frequency and severity of weather hazards and property insurance policies and prices.
+The study emphasizes the catastrophic impact of natural disasters on homeowners and the insurance industry. The financial burden 
+falls on homeowners, who must manage insurance premiums, deductibles, and coverage limitations. Likewise, insurance companies face 
+increased risks, threatening their financial stability.
 
-The importance of this study is the fact that weather disasters can carry profound amount of consequences, which affects the individual 
-homeowners and the insurance industry as a whole. Homeowners are the ones who typically bear the financial burden of disasters, and face 
-the finance of all the insurance premiums, deductibles, and coverage limitations at the same time. On the other hand, the insurance 
-company is tasked to manage the increased risks associated with these events, which can also have a significant impact on their financial 
-stability.
+While previous research has touched on weather risks and insurance prices, our study delves deeper into the dynamics of frequency and 
+severity in property insurance pricing, based on valuable insights \cite{hurricaneeco}. We want to find effective ways to reduce the financial burden 
+on homeowners during major disasters.
 
-While previous research has examined different aspects of this complex issue, including the impact of weather risks on insurance 
-prices, there are much more waiting to be discovered. Our research is based on valuable insights into the value of previous work 
-\cite{hurricaneco} aimed at assets that have provided insurance pricing of weather frequency and severity. It provides a general 
-understanding of how frequency and severity affect the pricing of property insurance. We are also trying to identify effective 
-strategies that can reduce the financial burden of homeowners in the face of these major disasters.
-
-This research has used several methods, including statistical analysis and data science methods. To achieve our goals, we will draw 
-data from reliable sources, such as the Insurance Information Agency, National Insurance Centers for Environmental Informations, and 
-Aon's 2023 Weather, Climate and Disaster Investigation Report. This study is not only timely but critically important at a time of 
-increasing weather-related risks, with the goal of contributing to homeowner well-being and the stability of the property insurance 
-market.
+We draw data from reliable sources such as the Insurance Information Agency, National Insurance Centers for Environmental Information, 
+and Aon's 2023 Weather, Climate, and Disaster Investigation Report using statistical analysis and data science. This study aims to 
+improve homeowner well-being and the stability of the property insurance market in the face of rising weather-related risks.
 
@@
 reliability in documenting catastrophic events and their associated economic and insured losses.
+
+These data sources, sourced from leading insurance analytics firms and research organizations, provide an important foundation and 
+context for assessing the relationship between intensifying extreme weather events and rising property insurance costs. Using decades 
+of specialized knowledge to track climate impacts and pricing trends across vulnerable geographies.
+
+Aon is at the forefront of risk analysis in the insurance industry, with dedicated catastrophe model development and annual global 
+climate reports tracking disaster losses. This establishes Aon as an unrivaled resource for linking increasing weather perils to 
+property insurance pricing trends.
+
+The Insurance Information Institute (III), a trusted insurance trade group, provides proprietary research and public education on aligning 
+property insurance costs with escalating climate risks confronting communities across risk-prone regions.
+
+The National Centers for Environmental Information (NCEI) provides data backbone to guide evidence-based assessment of how record-breaking 
+weather extremes are translating to property insurance market dynamics by maintaining the nation's authoritative disaster cost 
+database.
+
+The National Association of Insurance Commissioners (NAIC) facilitates transparency from insurers on pricing and product shifts caused by 
+worsening climate factors such as hurricanes, flooding, and wildfires through regulatory oversight across states, structured data 
+calls, and cross-collaborations.
 
@@
 
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.8\linewidth]{NCEI US disaster freq.pdf}
-    \label{fig:disaster_freq}
-    \cite{ncei}
-\end{figure}
-
-This chart \ref{fig:disaster_freq} shows the percentage frequency of years from 1980-2023 that experienced different numbers of billion-dollar disasters. It 
-looks at years with 1 or more, up to 5 or more billion-dollar disaster events. The chart helps to characterize the concentration and 
-frequency of multiple disasters in a single year.
-
 \begin{table}[h]
@@
 \end{table}
+
+This chart \ref{fig:disaster_freq} shows the percentage frequency of years from 1980-2023 that experienced different numbers of billion-dollar disasters. It 
+looks at years with 1 or more, up to 5 or more billion-dollar disaster events. The chart helps to characterize the concentration and 
+frequency of multiple disasters in a single year.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.8\linewidth]{NCEI US disaster freq.pdf}
+    \label{fig:disaster_freq}
+    \cite{ncei}
+\end{figure}
 
@@
 
+This figure \ref{fig:disaster_threats} shows the cumulative billion-dollar disaster costs in the United States from 1980-2023 on a year-to-date basis. It 
+illustrates how annual disaster costs accumulate through the year, with key major disaster event years highlighted. The table 
+provides context on total disaster costs over time.
+
 \begin{figure}[ht]
@@
 
-This figure \ref{fig:disaster_threats} shows the cumulative billion-dollar disaster costs in the United States from 1980-2023 on a year-to-date basis. It 
-illustrates how annual disaster costs accumulate through the year, with key major disaster event years highlighted. The table 
-provides context on total disaster costs over time.
+This figure \ref{fig:regional_disasters} shows the number of billion-dollar disaster events by type in the United States from 1980-2023. It breaks down event counts 
+for droughts, flooding, freezes, severe storms, tropical cyclones, wildfires, and winter storms. The total disaster cost is also shown 
+accumulated across years. The chart gives overview insight into disaster frequency and cost by peril.
 
@@
 
-This figure \ref{fig:regional_disasters} shows the number of billion-dollar disaster events by type in the United States from 1980-2023. It breaks down event counts 
-for droughts, flooding, freezes, severe storms, tropical cyclones, wildfires, and winter storms. The total disaster cost is also shown 
-accumulated across years. The chart gives overview insight into disaster frequency and cost by peril.
+As evidenced by this chart \ref{fig:10economic_loss} of the ten most expensive global insured catastrophe losses from 1900 to 2022, 
+the rising frequency and severity of extreme weather events in the last two decades has increased the risks and costs for property 
+insurers. Hurricanes that have ravaged North America and the Caribbean in recent years have caused almost all of the disasters, with 
+seven of the ten occurring in the last 15 years. The confluence of billion-dollar hurricane disasters, as well as rapidly rising 
+nominal and inflation-adjusted insured losses, highlight the insurance industry's mounting climate-change costs. With three of the 
+four largest loss events occurring in 2021-2022 alone, property insurers face escalating climate threats and exposures that 
+necessitate significant adjustments to rates, coverages, and risk mitigation efforts in especially vulnerable coastal and island 
+regions. Addressing these challenges through preventative resilience initiatives and innovative insurance solutions will be critical 
+to enabling the industry to cover the property landscape of the future in a viable and sustainable manner.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.8\linewidth]{AON Top 10 Cyclones Economic Loss.pdf}
+    \label{fig:10economic_loss}
+    \cite{aon}
+\end{figure}
+
+This chart \ref{fig:10global_loss} of the top ten most economically destructive tropical cyclones in the world from 1900 to 2022 emphasizes the growing risks 
+that hurricanes pose in a changing climate. With the United States being hit by all ten of the costliest storms since 2000, the trend 
+toward repeated devastating hurricane seasons is clear and concerning for coastal communities. The clustering of five massive 
+back-to-back hurricane events in the last six years, putting unprecedented strain on the US economy, lends credence to modeling that 
+suggests tropical storms are becoming more destructive. Hurricane vulnerability and recovery costs will only increase as sea levels 
+rise and waters warm, exposing more property than ever before.  This necessitates immediate action across the public and private 
+sectors to strengthen pre-disaster mitigation and post-disaster resilience if the already record-breaking cost of hurricanes is not 
+to skyrocket in the future. To address this escalating climate threat, innovative policy, infrastructure, community design, and 
+financing tools must be combined.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.8\linewidth]{AON Top 10 Global Insured Loss.pdf}
+    \label{fig:10global_loss}
+    \cite{aon}
+\end{figure}
 
@@
 
+In order to isolate the relationships between disaster activity and average homeowners insurance premiums over time, we used 
+panel regression techniques with state and year-fixed effects. To reduce omitted variable bias, models specifically control for 
+time-invariant differences across states (via state dummies) as well as national trends (via year indicators). The premium measure is 
+the dependent variable, with the key independent variables being disaster counts and cost totals.
+
+These disaster measures capture state-specific exposure each year, providing granular, longitudinal pricing connectivity. Taking logs 
+accounts for skewness and simplifies elasticity interpretation. We anticipate that worsening loss shocks will have a direct impact on 
+insurers' underwriting decisions, resulting in measurable premium impacts. Differential sensitivity testing is possible by segmenting 
+by peril type.
+
 Given the skewed distribution of disaster cost variables, logs are used. Fixed effects by state and year account for time-dependent 
@@
 highlighting the irregular nature of extremes. Hurricane and flooding perils account for the largest share of overall cost and 
-insured losses.
+insured losses. The regression results show that increasing natural disaster activity plays a statistically significant role in 
+driving increases in homeowners insurance premiums across risk-exposed states. According to the elasticity estimates, premiums grow 
+at a higher percentage rate than disaster costs.
 
@@
     \caption{Summary Statistics}
-    \cite{statista, ncai, fema}
+    \cite{statista, ncei, FEMA}
 \end{table}
@@
 associated with higher premiums based on the log-log specification. A 10\% increase in disasters corresponds to a 14.7\% rise in 
-premiums. Meanwhile, a 10\% rise in total damage leads to a 23.1\% premium increase.
+premiums. Meanwhile, a 10\% rise in total damage leads to a 23.1\% premium increase. In other words, 10\% increase in total catastrophe 
+damages incurred in a state-year, for example, corresponds to a 23.1\% increase in annual average premiums. This emphasizes the 
+exponentially rising underwriting risks and loss adjustments made by insurers based on compounding extreme event data.
 
@@
 
-    \cite{statista, ncai}
+    \cite{statista, ncei}
   \end{table}
@@
   substantial impacts on insurance premiums. Specifically, a 10\% increase in hurricane or flood Damages are associated with 
-  approximately a 0.01\% increase in premiums. Severe storms and winter weather also exhibit positive effects on premiums. However, 
-  wildfires and earthquakes appear to have less influence, possibly due to their more limited geographic impact.
+  approximately a 0.01\% increase in premiums. Results also show that hurricanes and flooding disasters have a disproportionate 
+  impact in comparison to other hazards. Climate change appears to be worsening exposure along the coast and in low-lying areas. 
+  Additional findings indicate that winter storms may necessitate price changes in some states. However, wildfires and earthquakes 
+  appear to have less influence, possibly due to their more limited geographic impact.
 
@@
 
-    \cite{statista, ncai}
+    \cite{statista, ncei}
   \end{table}
+
+  These panel regressions provide empirical evidence that worsening extremes are increasing premiums in line with rising expected loss 
+  trends. Strategic risk-reduction policies will be critical in the future.
 

### 2023-12-11 manuscript/manuscript.tex
modified pdf
made more concise, remove redundancy

--- 2023-11-07 manuscript/manuscript.tex
@@
 
+% double spacing
+\usepackage{setspace}
+\doublespacing
+
 \title{The Impact of Extreme Weather Events on Property Insurance Pricing}
@@
 \begin{abstract}
-Weather catastrophes, like hurricanes, wildfires, hail storms, etc., have become more common and severe in recent years, which poses 
-significant risks to homeowners and has significant financial consequences. The purpose of this research paper is to look into the 
-impact of weather catastrophe frequency and severity on property insurance policy prices, and also, to identify strategies for easing 
-the financial burden on homeowners. This research combines statistical analysis and data science techniques, drawing on data from 
-reliable sources such as the Insurance Information Institute and Aon's 2023 Weather, Climate, and Catastrophe Insight Report. The 
-research aims to provide helpful insights into the relationships between the frequency and severity of weather catastrophes and 
-property insurance pricing in order to inform insurance industry practices and public policy decisions to improve resilience to 
-catastrophes.
+    In recent years, the increasing severity of weather disasters like hurricanes, wildfires, and hail storms and 
+    their impact on homeowners and their finances. It explores how the frequency and severity of these catastrophes influence property 
+    insurance prices. Using statistical analysis and data from reliable sources such as the Insurance Information Institute and Aon's 
+    2023 Weather, Climate, and Catastrophe Insight Report, the study aims to provide practical insights. These insights aim to inform 
+    both insurance industry practices and public policy decisions, focusing on improving resilience to such catastrophes and easing 
+    the financial burden on homeowners.
 \end{abstract}
@@
 \label{sec:intro}
-In recent years, weather catastrophes have become more frequent and severe, which poses a potential threat to homeowners' safety as 
-well as financial impacts. As the frequency and severity of disasters increase, the significance of the ability of homeowners to 
-protect their homes using property insurance also increases. This research will focus on exploring the relationship between the 
-frequency and severity of weather catastrophes and the pricing of property insurance.
+As the frequency and severity of weather catastrophe increased in recent years, it has been shown to pose threats to homeowners' 
+safety and finance as well. The study explores the rising frequency and severity of recent weather disasters, threatening homeowners' 
+safety and finances. It investigates their impact on property insurance pricing, emphasizing the catastrophic consequences for 
+homeowners and insurers. Managing insurance premiums, deductibles, and coverage limitations becomes challenging for homeowners, 
+while insurers face heightened financial risks.
 
-Climate disasters have become more frequent and severe in recent years. These incidents not only put homeowners' safety at risk but 
-also have significant economic consequences. As weather-related risks increase in frequency and severity, the ability for homeowners to 
-protect their valuable assets through property insurance has also become increasingly important This paper aims to explore the 
-relationship between the frequency and severity of weather hazards and property insurance policies and prices.
-
-The importance of this study is the fact that weather disasters can carry profound amount of consequences, which affects the individual 
-homeowners and the insurance industry as a whole. Homeowners are the ones who typically bear the financial burden of disasters, and face 
-the finance of all the insurance premiums, deductibles, and coverage limitations at the same time. On the other hand, the insurance 
-company is tasked to manage the increased risks associated with these events, which can also have a significant impact on their financial 
-stability.
-
-While previous research has examined different aspects of this complex issue, including the impact of weather risks on insurance 
-prices, there are much more waiting to be discovered. Our research is based on valuable insights into the value of previous work 
-\cite{hurricaneco} aimed at assets that have provided insurance pricing of weather frequency and severity. It provides a general 
-understanding of how frequency and severity affect the pricing of property insurance. We are also trying to identify effective 
-strategies that can reduce the financial burden of homeowners in the face of these major disasters.
-
-This research has used several methods, including statistical analysis and data science methods. To achieve our goals, we will draw 
-data from reliable sources, such as the Insurance Information Agency, National Insurance Centers for Environmental Informations, and 
-Aon's 2023 Weather, Climate and Disaster Investigation Report. This study is not only timely but critically important at a time of 
-increasing weather-related risks, with the goal of contributing to homeowner well-being and the stability of the property insurance 
-market.
+Unlike prior research \cite{hurricaneeco}, our study delves deeper into the dynamics of frequency and severity in property insurance 
+pricing, seeking effective ways to alleviate the financial burden during major disasters. Drawing data from reliable sources—such as 
+the Insurance Information Agency, National Insurance Centers for Environmental Information, and Aon's 2023 Weather, Climate, and 
+Disaster Investigation Report—we employ statistical analysis and data science techniques. The objective is to enhance homeowner 
+well-being and ensure stability in the property insurance market amidst increasing weather-related risks.
 
@@
 \label{sec:data}
-To comprehend the impact of weather-related catastrophic events on property insurance pricing, we will begin by examining a dataset of 
-billion-dollar disasters. This dataset provides crucial information on event frequency, financial cost, and other key parameters. Our 
-data sources include the National Centers for Environmental Information (NCEI)\cite{ncei}, the Insurance Information Institute 
-(III)\cite{iii}, Aon\cite{aon} and the National Association of Insurance Commissioners (NAIC)\cite{naic}, all are recognized for their 
+In order to understand the impact of weather catastrophe on property insurance pricing, we will first look at a dataset of 
+billion-dollar disasters. This dataset contains important information about the frequency, financial cost, and some other parameters. 
+Our data sources include the National Centers for Environmental Information (NCEI)\cite{ncei}, the Insurance Information Institute 
+(III)\cite{iii}, Aon\cite{aon} and the National Association of Insurance Commissioners (NAIC)\cite{naic}, which are all known for their 
 reliability in documenting catastrophic events and their associated economic and insured losses.
 
+These data sources are all sourced from leading insurance analytics firms and research organizations. They provide an important foundation and 
+context for assessing the relationship between extreme weather events and rising property insurance costs. Here is a little background
+for the sources of the dataset:
+
+Aon is at the forefront of risk analysis in the insurance industry, with dedicated catastrophe model development and annual global 
+climate reports tracking disaster losses. This establishes Aon as an unrivaled resource for linking increasing weather perils to 
+property insurance pricing trends.
+
+The Insurance Information Institute (III), a trusted insurance trade group, provides proprietary research and public education on aligning 
+property insurance costs with escalating climate risks confronting communities across risk-prone regions.
+
+The National Centers for Environmental Information (NCEI) provides data backbone to guide evidence-based assessment of how record-breaking 
+weather extremes are translating to property insurance market dynamics by maintaining the nation's authoritative disaster cost 
+database.
+
+The National Association of Insurance Commissioners (NAIC) facilitates transparency from insurers on pricing and product shifts caused by 
+worsening climate factors such as hurricanes, flooding, and wildfires through regulatory oversight across states, structured data 
+calls, and cross-collaborations.
+
 Our primary dataset, obtained from the National Centers for Environmental Information (NCEI)\cite{ncei}, spans between the years from 
-1980 to 2023. We have organized the data into various temporal segments to facilitate analysis. Table \ref{tab:bil_dol_disasters} 
-summarizes key statistics from this dataset, which provides insights into the frequency of catastrophic events, total financial cost, and 
-associated fatalities. These temporal segments, ranging from the 1980s to the present day, enable us to assess trends over time and 
-help to identify potential patterns.
+1980 to 2023. We have organized the data into various temporal segments to facilitate the analysis. Table \ref{tab:bil_dol_disasters} 
+summarizes key statistics from this dataset, which provides insights into the frequency of the catastrophic events, total financial cost, and 
+associated fatalities. These temporal segments allows us to assess trends over time and help to identify potential patterns.
 
@@
 
-To further examine the financial implications of natural disasters, we turn to the Insurance Information Institute (III)\cite{iii}. 
-Table \ref{tab:natural_cat_losses} for the year 2022 provides a breakdown of catastrophic events by peril, including data on the 
-number of events, fatalities, economic losses, and insured losses. This granular information is essential for understanding the 
-varying impacts of different types of natural catastrophes and their associated costs.
-
-\begin{figure}[ht]
-    \centering
-    \includegraphics[width=0.8\linewidth]{NCEI US disaster freq.pdf}
-    \label{fig:disaster_freq}
-    \cite{ncei}
-\end{figure}
-
-This chart \ref{fig:disaster_freq} shows the percentage frequency of years from 1980-2023 that experienced different numbers of billion-dollar disasters. It 
-looks at years with 1 or more, up to 5 or more billion-dollar disaster events. The chart helps to characterize the concentration and 
-frequency of multiple disasters in a single year.
+To further examine the financial implications of natural disasters, we will turn to the Insurance Information Institute (III)\cite{iii}. 
+Table \ref{tab:natural_cat_losses} provides a breakdown of catastrophic events by specific perils for the year 2022, including data on the 
+number of events, fatalities, economic losses, and insured losses. Through these informations, we will gain a better understanding of the 
+varying impacts of different types of weather catastrophes and the associated costs.
 
@@
 
-The Insurance Information Institute (III) \cite{iii} also supplies data on insured property losses in the United States for the years 
-2013-2022. Table \ref{tab:insured_prop_losses} presents both the nominal loss values when the events occurred and their equivalent 
-values in 2022 dollars. Analyzing this information will allow us to assess how insured losses have evolved over the past decade.
+The chart \ref{fig:disaster_freq} shows the percentage frequency, of the years from 1980-2023, that experienced different numbers of 
+billion-dollar disasters. It examines at years with 1 or more, up to 5 or more billion-dollar disaster events. The chart helps to 
+characterize the concentration and frequency of multiple disasters in a single year.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.8\linewidth]{NCEI US disaster freq.pdf}
+    \label{fig:disaster_freq}
+    \cite{ncei}
+\end{figure}
+
+The Insurance Information Institute (III) \cite{iii} also provides data on insured property losses in the United States for the years 
+from 2013-2022. Table \ref{tab:insured_prop_losses} presents both the nominal loss values when the events occurred and their equivalent 
+(inflated) values in 2022 dollars. Analyzing this information will allow us to assess how insured losses have evolved over the past decade.
 
@@
 
+The figure \ref{fig:disaster_threats} shows the cumulative billion-dollar disaster costs in the United States from 1980-2023 on a year-to-date basis. It 
+illustrates how annual disaster costs accumulate through the year, with key major disaster event years highlighted. The table 
+provides context on total disaster costs over time.
+
 \begin{figure}[ht]
@@
 
-This figure \ref{fig:disaster_threats} shows the cumulative billion-dollar disaster costs in the United States from 1980-2023 on a year-to-date basis. It 
-illustrates how annual disaster costs accumulate through the year, with key major disaster event years highlighted. The table 
-provides context on total disaster costs over time.
+The figure \ref{fig:regional_disasters} shows the number of billion-dollar disaster events by type in the United States from 1980-2023. It breaks down event counts 
+for droughts, flooding, freezes, severe storms, tropical cyclones, wildfires, and winter storms. The total disaster cost is also shown 
+accumulated across years. The chart gives overview insight into disaster frequency and cost by peril.
 
@@
 
-This figure \ref{fig:regional_disasters} shows the number of billion-dollar disaster events by type in the United States from 1980-2023. It breaks down event counts 
-for droughts, flooding, freezes, severe storms, tropical cyclones, wildfires, and winter storms. The total disaster cost is also shown 
-accumulated across years. The chart gives overview insight into disaster frequency and cost by peril.
+The chart \ref{fig:10economic_loss} presents the ten most expensive global insured catastrophe losses from 1900 to 2022, highlighting 
+the rising risks and costs that property insurers are facing. The chart highlights the insurance industry's climate-change costs, which 
+require immediate adjustments to rates, coverages, and risk-mitigation efforts, with a focus on vulnerable coastal and island regions.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.8\linewidth]{AON Top 10 Cyclones Economic Loss.pdf}
+    \label{fig:10economic_loss}
+    \cite{aon}
+\end{figure}
+
+The chart \ref{fig:10global_loss} showing the top ten economically destructive tropical cyclones worldwide from 1900 to 2022 
+highlights the increasing risks posed by hurricanes in a changing climate. In particular, the United States has been hit by all ten 
+of the costliest storms since 2000, suggesting a concerning trend of recurring severe hurricane seasons for coastal regions.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.8\linewidth]{AON Top 10 Global Insured Loss Events.pdf}
+    \label{fig:10global_loss}
+    \cite{aon}
+\end{figure}
 
@@
 To better understand the relationships between weather catastrophes, property insurance, and financial impact, we will first introduce 
-several key equations that will act as a basis to guide our analysis:
+several key equations that will act as a general basis to guide our analysis:
 
@@
 
-The premium equation \ref{eq:premium} calculates the estimated premium based on the frequency, severity, and exposure units. This 
-reflects the financial implications for homeowners and insurers.
+The premium equation \ref{eq:premium} calculates the estimated premium based on the frequency, severity, and exposure units, which 
+shows the financial consequences for both homeowners and insurance companies.
 
-We hope to gain a thorough understanding of the complex relationship between weather-related disasters and property insurance pricing 
-by understanding these fundamental equations. These equations will serve as a basis for our data analysis, allowing us to effectively 
-assess the impact of catastrophic events on property insurance while also assisting us in meeting our research objectives.
+By understanding these fundamental equations, we hope to gain a thorough understanding of the relationship between weather-related disasters 
+and property insurance pricing. Like mentioned earlier, these equations will serve as a basis for our data analysis, allowing us to 
+effectively assess the impact of catastrophic events on property insurance while also assisting us in meeting our research objectives.
 
-This comprehensive dataset, supported by granular data from the Insurance Information Institute \cite{iii}, serves as the foundation 
-for our research. The various chronological segments, as well as the key equations, provide us with the resources that we need to 
-delve deeper into the impact of weather-related catastrophes on property insurance, allowing us to effectively address our research 
-objectives.
+This comprehensive dataset, supported by data from the Insurance Information Institute \cite{iii}, serves as the foundation 
+for our research, while incorporating other data for support from other sources as well. The various chronological segments, as well 
+as the key equations, provide us with the resources that we need to delve deeper into the impact of weather-related catastrophes on 
+property insurance, allowing us to effectively address our research objectives.
 
@@
 
-Given the skewed distribution of disaster cost variables, logs are used. Fixed effects by state and year account for time-dependent 
-differences between states and national trends. We begin by looking at the impact of aggregated disaster activity. The models are then 
-estimated by interacting the disaster measures with peril indicators in order to compare the sensitivity across event types. Quantile 
-regression was also used to determine whether or not effects differ across the premium distribution.
+In order to isolate the relationships between disaster events and average homeowners insurance premiums over time, we will use 
+panel regression techniques with state and year-fixed effects as the key variables or factors. To reduce omitted variable bias, 
+models specifically control for time-invariant differences across states (the state dummies) as well as national trends (the year 
+indicators). The premium measure acts as the dependent variable, with the key independent variables being disaster counts and 
+cost totals.
+
+Each year, these disaster measures capture state-specific exposure, which allows for more precise pricing connectivity over time. Taking logs 
+accounts for skewness and simplifies elasticity interpretation. We anticipate that worsening loss shocks will have a direct impact on 
+insurers' underwriting decisions, resulting in measurable premium impacts. By measuring different peril types, differential sensitivity testing 
+may be possible through segmentation.
 
@@
 \subsection{Summary Statistics}
-Table 4 \ref{tab:summary} presents summary statistics for the premium and disaster data. The disaster measures show substantial variability, 
-highlighting the irregular nature of extremes. Hurricane and flooding perils account for the largest share of overall cost and 
-insured losses.
+Table \ref{tab:summary} presents summary statistics for the premium and disaster data. The disaster measures show substantial variability, 
+highlighting the irregular nature of extremes. Specifically, hurricane and flooding perils account for the largest proportion of the overall cost and 
+insured losses. The regression results show that increasing natural disaster events plays a statistically significant role in 
+driving increases in homeowners insurance premiums across risk-exposed states (e.g. coastal ones). According to the elasticity estimates, premiums grow 
+at a higher percentage rate than disaster costs.
 
@@
 \subsection{Regression Results}
-Table 5 \ref{tab:reg_results} presents results from the panel regressions. The number of disasters and total cost are significantly 
+Table \ref{tab:reg_results} presents results from the panel regressions. The number of disasters and total cost are significantly 
 associated with higher premiums based on the log-log specification. A 10\% increase in disasters corresponds to a 14.7\% rise in 
-premiums. Meanwhile, a 10\% rise in total damage leads to a 23.1\% premium increase.
+premiums. Meanwhile, a 10\% rise in total damage leads to a 23.1\% premium increase. In other words, 10\% increase in total catastrophe 
+damages incurred in a state-year corresponds to a 23.1\% increase in annual average premiums. This emphasizes the 
+exponentially rising underwriting risks and loss adjustments made by insurers based on compounding extreme event data.
 
@@
 
-    \cite{statista, ncai}
+    \cite{statista, ncei}
   \end{table}
 
-  The results presented in Table 6 \ref{tab:reg_peril} indicate that hurricane and flood disasters have the most 
-  substantial impacts on insurance premiums. Specifically, a 10\% increase in hurricane or flood Damages are associated with 
-  approximately a 0.01\% increase in premiums. Severe storms and winter weather also exhibit positive effects on premiums. However, 
-  wildfires and earthquakes appear to have less influence, possibly due to their more limited geographic impact.
+  The results presented in Table \ref{tab:reg_peril} indicate that hurricane and flood disasters, mentioned earlier \ref{tab:summary}, 
+  have the most substantial impacts on insurance premiums. Specifically, a 10\% increase in hurricane or flood damages associates with 
+  approximately a 0.01\% increase in premiums. Results also show that hurricanes and flooding disasters have a disproportionate 
+  impact in comparison to other hazards. Additional findings indicate that winter storms may necessitate price changes in some states. 
+  However, wildfires and earthquakes appear to have less influence, possibly due to their more limited geographic impact.
 
@@
 
-    \cite{statista, ncai}
+    \cite{statista, ncei}
   \end{table}
+
+  These panel regressions all provide empirical evidence that worsening extremes are increasing premiums in line with rising expected loss 
+  trends. Strategic risk-reduction policies will be important in the future.
 
@@
 
-The study found a statistically significant link between extreme weather events and homeowner insurance pricing. According to the 
+The study found a statistically significant relationship between extreme weather events and homeowner insurance pricing. According to the 
 results, more frequent and severe events are associated with higher premiums, especially for hurricanes and flooding perils. This is 
@@
 
-However, there are limitations to the data collected. Analytics may benefit from having more granular, address-level premium data to 
+However, there are limitations to the data collected. Analytics may benefit from having more precise premium data to 
 better pinpoint local hazards. In addition, the model fails to take account of changes in exposures and vulnerabilities over time as risk 
@@
 
-Still, these results demonstrate an interrelation between catastrophic incidents and rising property insurance premiums - two trends 
-with many causes and effects that overlap significantly. As climate change intensifies weather extremes, homeowners could face 
-financial strain - potentially undermining the stability of insurance markets and leading to economic instability for policy 
+Still, these results demonstrate an interrelation between weather catastrophe incidents and rising property insurance premiums - which are 
+two trends with many causes and effects that overlap significantly. As climate change intensifies weather extremes, homeowners could 
+face financial strain - potentially undermining the stability of insurance markets and leading into economic instability for policy 
 interventions like subsidized insurance policies\cite{iii}, resilience incentives, or residential investments\cite{kousky} that 

### 2023-12-11 manuscript/manuscript.tex
more redundancy removed and modified for easy reading

@@
 \begin{abstract}
-    In recent years, the increasing severity of weather disasters like hurricanes, wildfires, and hail storms and 
-    their impact on homeowners and their finances. It explores how the frequency and severity of these catastrophes influence property 
-    insurance prices. Using statistical analysis and data from reliable sources such as the Insurance Information Institute and Aon's 
-    2023 Weather, Climate, and Catastrophe Insight Report, the study aims to provide practical insights. These insights aim to inform 
-    both insurance industry practices and public policy decisions, focusing on improving resilience to such catastrophes and easing 
-    the financial burden on homeowners.
+    In recent years, with frequency and severity of weather catastrophes both increasing, it has been shown to make a significant impact 
+    on homeowners as well as making a financial burden. We will be exploring how the frequency and severity of these catastrophes 
+    influence property insurance prices through statistical analysis and data from reliable sources, such as the Insurance Information 
+    Institute and Aon's 2023 Weather, Climate, and Catastrophe Insight Report. The objective of this study aims to provide practical 
+    insights to inform both insurance industry practices and public policy decisions, in addition to focusing on improving resilience 
+    to such catastrophes and easing the financial burden on homeowners.
 \end{abstract}
@@
 \label{sec:intro}
-As the frequency and severity of weather catastrophe increased in recent years, it has been shown to pose threats to homeowners' 
-safety and finance as well. The study explores the rising frequency and severity of recent weather disasters, threatening homeowners' 
-safety and finances. It investigates their impact on property insurance pricing, emphasizing the catastrophic consequences for 
-homeowners and insurers. Managing insurance premiums, deductibles, and coverage limitations becomes challenging for homeowners, 
-while insurers face heightened financial risks.
+As the frequency and severity of weather catastrophe increase, it is shown to pose threats to homeowners' safety and finance.
+It investigates their impact on property insurance pricing, emphasizing the catastrophic consequences for homeowners and insurers. 
+Managing insurance premiums, deductibles, and coverage limitations becomes challenging for homeowners, while insurers face massive 
+financial risks.
 
-Unlike prior research \cite{hurricaneeco}, our study delves deeper into the dynamics of frequency and severity in property insurance 
-pricing, seeking effective ways to alleviate the financial burden during major disasters. Drawing data from reliable sources—such as 
+Unlike prior research \cite{hurricaneeco}, our study dives deeper into the dynamics of frequency and severity in property insurance 
+pricing, seeking effective ways to alleviate the financial burden during major disasters. Drawing data from reliable sources,
 the Insurance Information Agency, National Insurance Centers for Environmental Information, and Aon's 2023 Weather, Climate, and 
-Disaster Investigation Report—we employ statistical analysis and data science techniques. The objective is to enhance homeowner 
-well-being and ensure stability in the property insurance market amidst increasing weather-related risks.
-
-The rest of the paper is organized as follows.
-The data will be presented in Section~\ref{sec:data}.
-The methods are described in Section~\ref{sec:meth}.
-The results are reported in Section~\ref{sec:resu}.
-A discussion concludes in Section~\ref{sec:disc}.
+Disaster Investigation Report — where we will use statistical analysis and data science techniques. The objective is to enhance 
+the well-being of homeowners and ensure the stability in the property insurance market against the increasing weather-related risks.
 
@@
 \label{sec:data}
-In order to understand the impact of weather catastrophe on property insurance pricing, we will first look at a dataset of 
-billion-dollar disasters. This dataset contains important information about the frequency, financial cost, and some other parameters. 
-Our data sources include the National Centers for Environmental Information (NCEI)\cite{ncei}, the Insurance Information Institute 
-(III)\cite{iii}, Aon\cite{aon} and the National Association of Insurance Commissioners (NAIC)\cite{naic}, which are all known for their 
-reliability in documenting catastrophic events and their associated economic and insured losses.
+In order to understand the impact of weather catastrophe on property insurance pricing, we will first look at a dataset that 
+contains important information about the frequency, financial cost, and some other parameters. Our data sources are drawn from 
+National Centers for Environmental Information (NCEI)\cite{ncei}, the Insurance Information Institute (III)\cite{iii}, Aon\cite{aon} 
+and the National Association of Insurance Commissioners (NAIC)\cite{naic}, which are all well known for their reliability in 
+documenting catastrophic events and their associated economic and insured losses.
 
@@
 
-The figure \ref{fig:disaster_threats} shows the cumulative billion-dollar disaster costs in the United States from 1980-2023 on a year-to-date basis. It 
-illustrates how annual disaster costs accumulate through the year, with key major disaster event years highlighted. The table 
-provides context on total disaster costs over time.
+The figure \ref{fig:disaster_threats} shows the cumulative billion-dollar disaster costs in the United States from 1980-2023. It 
+illustrates how annual disaster costs accumulate through the year, with highlighting the key disasters of the year. The table 
+also provides context on total disaster costs over time.
 
@@
 
-The figure \ref{fig:regional_disasters} shows the number of billion-dollar disaster events by type in the United States from 1980-2023. It breaks down event counts 
-for droughts, flooding, freezes, severe storms, tropical cyclones, wildfires, and winter storms. The total disaster cost is also shown 
-accumulated across years. The chart gives overview insight into disaster frequency and cost by peril.
+The figure \ref{fig:regional_disasters} shows the number of billion-dollar disaster events by specific perils in the United States 
+from 1980-2023.
 
@@
 
-The chart \ref{fig:10economic_loss} presents the ten most expensive global insured catastrophe losses from 1900 to 2022, highlighting 
-the rising risks and costs that property insurers are facing. The chart highlights the insurance industry's climate-change costs, which 
-require immediate adjustments to rates, coverages, and risk-mitigation efforts, with a focus on vulnerable coastal and island regions.
+The chart \ref{fig:10economic_loss} showing the top ten most expensive cyclone economic losses from 1900 to 2022, highlighting 
+the rising risks and costs that property insurers are facing. Specifically, the chart focuses on vulnerable coastal and island regions,
+which are known to be cyclone, hurricane, and flooding hazardous zones.
+The chart \ref{fig:10global_loss} presents the top ten most expensive global insured catastrophe losses from 1900 to 2022, highlighting
+the rising risks and costs that property insurers are facing.
 
@@
 \end{figure}
-
-The chart \ref{fig:10global_loss} showing the top ten economically destructive tropical cyclones worldwide from 1900 to 2022 
-highlights the increasing risks posed by hurricanes in a changing climate. In particular, the United States has been hit by all ten 
-of the costliest storms since 2000, suggesting a concerning trend of recurring severe hurricane seasons for coastal regions.
 
@@
     \label{eq:freq}
-    \text{Frequency} = \frac{\text{Number of Loss Events}}{\text{Exposure Units}}
+    \text{Frequency} = \frac{\text{Number of Loss Events}}{\text{Exposure}}
 \end{equation}
 
-The frequency equation \ref{eq:freq} calculates the frequency of loss events by dividing the number of loss events by exposure units.
+The frequency equation \ref{eq:freq} calculates the frequency by dividing the number of loss events by the exposure.
 
@@
     \label{eq:sev}
-    \text{Severity} = \frac{\text{Total Loss Amount}}{\text{Number of Loss Events}}
+    \text{Severity} = \frac{\text{Total Loss}}{\text{Number of Loss Events}}
 \end{equation}
 
-The severity equation \ref{eq:sev} is determined by dividing the total loss amount by the number of loss events.
-
-\begin{equation}
-    \label{eq:losscost}
-    \text{Loss Cost} = \text{Frequency} \times \text{Exposure Units}
-\end{equation}
-
-The loss count equation \ref{eq:losscost} is the product of frequency and exposure units, providing insights into the overall loss count due to catastrophic events.
+The severity equation \ref{eq:sev} calculates the severity by dividing the total loss by the number of loss events.
 
@@
     \label{eq:premium}
-    \text{Premium} = \lambda \cdot \text{Severity} \cdot \text{Exposure Units}
+    \text{Premium} = \lambda \cdot \text{Severity} \cdot \text{Exposure}
 \end{equation}
 
-The premium equation \ref{eq:premium} calculates the estimated premium based on the frequency, severity, and exposure units, which 
-shows the financial consequences for both homeowners and insurance companies.
+The premium equation \ref{eq:premium} calculates the estimated premium based on the frequency, severity, and exposure. This should be noted
+to be significant for both homeowners and insurance companies as it displays the financial consequences.
 
-By understanding these fundamental equations, we hope to gain a thorough understanding of the relationship between weather-related disasters 
-and property insurance pricing. Like mentioned earlier, these equations will serve as a basis for our data analysis, allowing us to 
-effectively assess the impact of catastrophic events on property insurance while also assisting us in meeting our research objectives.
+Through these key equations, we hope to gain a thorough understanding between the relationship of weather-related disasters 
+and property insurance pricing.
 
